### 2020-03-26 Article_file_Source_reconstruction.tex
Initial Overleaf Import

d
\documentclass[preprint,3p, 11pt,authoryear]{elsarticle}

\usepackage{graphicx}
\graphicspath{{./Graphic/}}
\usepackage{array}
\usepackage{amssymb} % various useful mathematical symbols
\usepackage{gensymb} % for `degree' sign
\usepackage{amsthm}  % extended theorem environments
\usepackage{lineno}   % for line numbers
\usepackage{tabularx} % for adjustable table width
\usepackage[hidelinks]{hyperref}  % for hyperlinks
\usepackage{amsmath}
\newtheorem{property}{Property}[section]
\usepackage{soul}
\usepackage{epsfig}
\usepackage{tabularx}
\usepackage{multirow} 
\usepackage{setspace}
\usepackage{adjustbox}
\usepackage{xcolor}

\journal{Nondestructive Testing and Evaluation}

\begin{document}

\begin{frontmatter}

\title{A methodology for calculating active source-time functions from broadband piezoelectric sensors in the laboratory}

 \author[1]{Paul A. Selvadurai \corref{cor1}}
 \ead{paul.selvadurai@sed.ethz.ch}
\author[2]{Rui Wu}
\author[3]{Claudio Madonna}

\cortext[cor1]{Corresponding author, Post-Doctoral fellow}
\address[1]{Swiss Seismological Service, ETH Zurich, Zurich, Switzerland}
\address[2]{Engineering Geology Group, ETH Zurich, Zurich, Switzerland}
\address[3]{Department of Earth Sciences, ETH Zurich, Zurich, Switzerland}

\begin{abstract}

\end{abstract}

\begin{keyword}
Acoustic emissions, absolutely calibrated sensors, active source time function, empirical Green's functions
\end{keyword}
\end{frontmatter}

\doublespacing
\linenumbers
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{int}

\section{Experimental facilities}
\subsection{General}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG1.pdf} 
\caption{\textbf{(a)}  }
	\label{fig1} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG2.pdf} 
\caption{\textbf{(a)}  }
	\label{fig2} 
\end{figure}

\subsection{Material properties}

\subsection{Elsys Instruments High-voltage Multiplexer}
***need information on \textbf{Piezosystem Jena HVP1000/100MODext.} from Roman Bertschi***

\section{Theory}
\label{theo}
We review the methodology that will model the forces produced by an active source piezoelectric transducer.  This methodology takes advantage of the theory surrounding elastodynamic wave propagation in an elastic medium.  We build on the recent studies of signal analysis and instrument calibration by \citet{McLaksey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}. We assume that wave propagation can be adequately described by convolution with the Green's function and that each component in our analysis can be modeled as a linear-time invariant system.  We are assuming that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations of both the sensor and source location. This so-called ``aperture'' effect is minimized by using the point contact conical PZT crystal but some deviations might be incurred.

Using the classical theory describing dynamic elasticity \citep{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$, which is given as the convolution of the force with the Green's function

\begin{equation}
\label{eq1}
           u_{k}\left( \mathbf{x}, t \right)  =  
            f_{j}\left( \mathbf{\xi}, \tau \right) \ast 
            g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right).
\end{equation}

\noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.  The true Green's function describes the displacement at time $t$ and location $\mathbf{x}$ for the unit impulse force at location $\mathbf{\xi}$ at the delayed time $\tau$.

Piezoelectric transducers measure a voltage caused by the compression of the lead zirconate titanate (PZT) crystal in the surface normal direction $s\left( \mathbf{x}, t \right)$. We can relate the true surface displacement $u_{k}$ to voltage measurement $s$ using the instrument response, which is given as

    \begin{equation}
    \label{eq2}
        s\left( \mathbf{x}, t \right) =
            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(t \right).
    \end{equation}

\noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the forces which produced them:

    \begin{equation}
    \label{eq3}
        s\left( \mathbf{x}, t \right) =
            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(t \right) =  
                f_{j}\left( \mathbf{\xi}, \tau \right) \ast 
                g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right) \ast i_{k}\left( t \right).
    \end{equation}

\noindent We can also use this formulation to relate the measured signals to a set of self-equilibrating forces or moments $m_{jp}$ \citep{Aki2002}. Displacements in the body are related to the spatial derivative of the elastodynamic Green's function $g_{kj,p}$.  While this is more similar to sources buried within a specimen and may be more representative of an earthquake source, this is not the focus of this study.  In this study, all sources are produced on the surface of the specimen, which justifies the use of only equation \eqref{eq2}.

Our study aims at determining the nature of the source produced that occurs we use the PZT crystal as active source. WE first decompose the source into two parts as shown here:

\begin{equation}
    \label{eq4}
    f_{j}\left( \mathbf{\xi}, \tau \right) = f^{*}_{j}\left( \mathbf{\xi}, \tau \right)  \ast \kappa \left( \tau \right),
\end{equation}

\noindent where $f^{*}_{j}$ is the normalized force-time function that has units (N) and a general shape to that follows the electro-mechanical behavior of the coupled high-voltage discharge and sensor systems.  A unitless scaling factor $\kappa$ will be used to scale the normalized force time-function $f^{*}$ to the true force-time function $f$ and likely varies with the time as the electrical pulse is applied to the active source.

We use properties of the Fourier transform \citep{Bracewell1986} to help deconvolve equations \eqref{eq3} and \eqref{eq4}.  In the frequency domain, convolution and deconvolution simply becomes multiplication and division. This allows us to isolate the components of interest we wish to quantify for our analysis. An example of the instrument response in the frequency domain $I_{w}$ simplifies to:

\begin{equation}
    \label{eq5}
        I_{k}\left(\omega \right) = 
        S\left( \mathbf{x}, \omega \right) \cdot \left[ F_{j}\left( \mathbf{\xi}, \hat{\omega} \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1} .
\end{equation}

\noindent where $I_{k}$, $S$, $F_{j}$ and $G_{kj}$ are calculated from the temporal Fourier transforms of the $i_{k}$, $s$, $f_{j}$ and $g_{kj}$, respectively.  As we will see in Section \ref{XXX}, instrument responses was calculated for the sensor array shown in Figure \ref{fig1}, where a controlled force-time function were applied at the central location by dropping small steel balls of different diameters onto the surface from a known height. According to Hertzian contact theory, it is possible to assume a source time function that is a function of the material properties of the ball and steel platen ($E, \nu, \rho$), the radius of ball, and the drop height. This method has been popularized over the recent years due to a highly reliable and repeatable force-time function $f$ produced from ball impact and the ability to absolutely calibrate the acoustic emission sensors over a wide spectral range \citep{McLaskey2010, McLaskey2012, McLaskey2015}.

We will use the known instrument response to better understand the source produced from the active PZT transducer.  We can rearrange equation \eqref{eq5} to obtain the true force in the frequency domain:

\begin{equation}
    \label{eq6}
\begin{split}
F_{j}\left( \mathbf{\xi}, \hat{\omega} \right) & = 
        S\left( \mathbf{x}, \omega \right) \cdot \left[ I_{k}\left(\omega \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1}, \\
\end{split}
\end{equation}

\noindent where by combing the Fourier transform of equation \eqref{eq4} we obtain an expression for the normalized force-time function,

\begin{equation}
    \label{eq7}
\begin{split}
F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right) & = 
        S\left( \mathbf{x}, \omega \right) \cdot \left[ K\left(\hat{\omega}\right) \cdot I_{k}\left(\omega \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1}.\\     
\end{split}
\end{equation}

\noindent To solve the features about $F^{*}_{j}$, we will need to \textit{a priori} knowledge of sensors instrument response, also needed will be signal measurements $S$ and the true Green's function $G_{kj}$ but we will still not know the frequency-dependent scaling function $K(\hat{\omega})$.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG3.pdf} 
\caption{\textbf{(a)}  }
	\label{fig3} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 0.90]{FIG4.pdf} 
\caption{\textbf{(a)}  }
	\label{fig4} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 0.9]{FIG5.pdf} 
\caption{\textbf{(a)}  }
	\label{fig5} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 0.9]{FIG6.pdf} 
\caption{\textbf{(a)}  }
	\label{fig6} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG7.pdf} 
\caption{\textbf{(a)}  }
	\label{fig7} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG8.pdf} 
\caption{\textbf{(a)}  }
	\label{fig8} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG9.pdf} 
\caption{\textbf{(a)}  }
	\label{fig9} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG10.pdf} 
\caption{\textbf{(a)}  }
	\label{fig10} 
\end{figure}

\section*{Acknowledgement}

\bibliographystyle{elsarticle-harv} 
\bibliography{Source_reconstruction}

\end{document}
\endinput

### 2020-04-03 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
-d
 \documentclass[preprint,3p, 11pt,authoryear]{elsarticle}
@@
 \usepackage{xcolor}
+\usepackage[utf8]{inputenc}
 
@@
 
-\noindent To solve the features about $F^{*}_{j}$, we will need to \textit{a priori} knowledge of sensors instrument response, also needed will be signal measurements $S$ and the true Green's function $G_{kj}$ but we will still not know the frequency-dependent scaling function $K(\hat{\omega})$.
+\noindent To solve the features about $F^{*}_{j}$, we will need to \textit{a priori} knowledge of sensors instrument response, also needed will be signal measurements $S$ and the true Green's function $G_{kj}$ but we will still not know the frequency-dependent scaling function $K(\hat{\omega})$ -- a primary calculation that is required to obtain the true force-time function produced by the active PZT transducer.
+
+\section{Results}
+\label{results}
+
+In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b).
+Waveforms have been color coded following Figure \ref{fig1}(b) to show measurements taken at similar epicentral distances.
+These waveform we produced by actively exciting the source sensor located at the top central location of the steel platen.
+For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen.
+This allows us to analyze the wave using the approximation that the plate is in fact semi-infinite.
+Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
+Figure \ref{fig3}(b) shows the empirical Green's functions (EGF) at a give epicentral location from the source.
+We call this the empirical Green's function since it is a numerical approximation of the true Green's function that is the resulting ground displacements $u$ at point $\mathbf{x}$ from a unit impulse function $\delta_{j}(\mathbf{\xi}, \tau)$.
+In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) for the numerical models.
 
@@
 \includegraphics[scale= 1.0]{FIG3.pdf} 
-\caption{\textbf{(a)}  }
+\caption{\textbf{(a)} Measurements on from passive PZT transducers from a source produced from the active sensor.
+The color scheme represents sensors at the different epicentral locations shown in Figure \ref{fig1}(b).
+\textbf{(b)} Green's function solutions using generalized ray theory for a semi-infinite elastic, homogeneous steel platen at different epicentral locations.
+The empirical Green's function (EGF) is equal to the true Green's function represents the displacements produced from the unit impulse force $\delta_{j}(\tau)$.
+We see the various phase arrival predicted from the model.}
 	\label{fig3} 
 \end{figure}
+
+Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.
+We show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) from the epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively.
+We see that the sensors appear to capture the multiple phase arrivals and this is believed to be due to the conical nature of the PZT crystal and its ability to capture wave arrivals at high azimuthal incident angles \citep{Selvadurai2019}.
+Results in Figure \ref{fig4} are representative of the measurements across all 13 passive sensors.
 
@@
 \includegraphics[scale= 0.90]{FIG4.pdf} 
-\caption{\textbf{(a)}  }
+\caption{Comparison of measurements on sensors A1, A2, A3 and A4 to the emipircal Green's functions calculated using generalized ray theory.
+The KRNBB sensor perform well and capture the wide range of wave phase arrivals.}
 	\label{fig4} 
@@
 
+To best show the approach we take to solve for the force time function produced by the active source, we focus on the measurements taken from sensors A3 at epicentral distance $x$ = 46 mm.
+Figure \ref{fig5}(a) shows the measurements and EGFs.
+We focus on detail B, which looks at the first arrival P wave.
+In Figure \ref{fig5}(b) this is shown in more detail with the sensors (green trace) and EGF (black trace) clearly visible.
+Since we know that, in the time domain, the signal produced on the sensors the force-time function are convolved with the associated Green's function, the shape of the specific wave with be representative of the source.
+The blue curve in Figure \ref{fig5}(b) is a best-guess approximation of the source and will be use to estimate the general normalized force-time function $f^{*}_{j}$ from equation \eqref{eq4}.
+
 \begin{figure}[ht]
      	\centering
-\includegraphics[scale= 0.9]{FIG5.pdf} 
-\caption{\textbf{(a)}  }
+\includegraphics[scale= 0.85]{FIG5.pdf} 
+\caption{\textbf{(a)} Measurements from sensor A3 (green line) from the active source compared to the EGFs at the same place from the model.
+Detail B looks more closely at the first-arrival P wave.
+\textbf{(b)} Shows the general shape of the P wave (green line) versus the location of the expected P wave arrival (black line) form the Green's function solution.
+From the convolutional nature of the wave propagation problem (equation \eqref{eq1}) we can estimate the general shape of the normalized force-time function $f^{*}_{j}$ shown as the blue line.}
 	\label{fig5} 
 \end{figure}
+
+\textbf{**Use Christensen (1988) to better define the force-time function**} We created the normalized force-time function based on characteristic of the first arrival P wave.
+In Figure \ref{fig5}(c) we show the methodology for generating $f^{*}_{j}$.
+We based this on the technical specifications of the high-voltage pulsing unit described in Section \ref{XXX}.
+In this experiment we applied a 100V pulse, which translates into a positive pulse, followed by a delay, then a negative pulse.
+We approximated this behavior using piecewise discontinuous step functions (red curve) that was convolved with a 0.6 $\mu$s triangle function to smoothen the step function.
+This produced the blue curve which matched the general shape of the P wave arrival in Figure \ref{fig5}(c).
+We will use this as a forward model to approximate the source-time from the active PZT source.
+We clearly see that the normalized force-time function varies from [-1,1], which is appropriate for our definition of $f^{*}$ in Section \ref{XXX}.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 0.9]{FIG5b.pdf} 
+\caption{\textbf{(a)}  }
+	\label{fig6} 
+\end{figure}
+
+To solve for the scaling function $K(\hat{\omega})$ we need to know the instrument response function $i(t)$.
+For this study, we use the results from \citet{Wu2020}.
+They performed multiple ball drops to create known force-time functions at the same location as the active sensors.
+The same sensors were used in their study and a series of different ball sizes where used (diameters = 0.3 mm, .....to 1.5 mm).
+\citet{Wu2020} modeled long times to also capture how the sensors responded to frequencies as low as $f$ =1 kHz, following the methodology by \citet{Wu2018}.
+Figure \ref{fig6}(a) shows the full instrument response function for each sensor in the Fourier domain (see equation \ref{eq5}).
+Figure \ref{fig6}(b) focuses only on the results for frequencies between $f$ = 100 kHz to 1000 kHz, which is more important to our understanding of the true force-time function in our case.
 
@@
 
+\clearpage
+
 \section*{Acknowledgement}
+T. M\"orgeli
 

### 2020-04-23 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 \author[3]{Claudio Madonna}
+\author[2]{Omid Moradian}
 
@@
 
+Understanding wave elastodynamic waves propagate through a medium has proven to have a multitude of applications in many fields of science and engineering.  
+\\
+
+Application in material science (crack detection), biomedics (ultrasonics), \textbf{more?} 
+\\
+The premise is to use well-understood physics associated with wave propagation, in fluids or solids media, to probe properties and assess its state in a non-destructive manner.
+
 \section{Experimental facilities}
@@
 \subsection{Material properties}
+
+\begin{table}[ht]
+	\centering
+	\caption{Material properties of HABA CK45 steel test platen.}
+	\begin{tabular}{ m{5cm} m{2cm} m{4cm}} 
+		\hline  
+		\bf{Parameter} 			& \bf{Symbol} 		& \bf{Value}	\\
+	    Density                 & $\rho$            & 7850 kg/m$^{3}$\\
+	    Shear modulus           & $\mu$             & 84 GPa \\
+	    Poisson's ratio         & $\nu$             & 0.28\\
+	    P wave velocity         & $V_{P}$           & 5890 m/s\\
+	    S wave velocity         & $V_{S}$           & 3270 m/s\\	    
+		\hline  	
+	\end{tabular}
+	\label{table1}
+\end{table}
 
@@
 
+\section*{Supplemental information}
+
+\begin{table}[ht]
+	\centering
+	\caption{Material properties of Piezoelectric active source (PZT-5A).}
+	\begin{tabular}{ m{5cm} m{2cm} m{4cm}} 
+		\hline  
+		\bf{Parameter} 		      & \bf{Symbol} 	  & \bf{Value}	\\
+	   & \textit{Mechanical properties} & \\
+	    Density                   & $\rho$            & 7500 kg/m$^{3}$\\
+	    Poisson's ratio           & $\nu$             & 0.31\\
+	    Young's modulus           & $E$               & 66 GPa\\
+        Curie Point               & $T_{c}$           & 350 $^{o}$C\\  
+        Mechanical quality factor &   $Q_{m}$         & 100\\
+	  & \textit{Piezoelectric constants} & \\
+ 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
+ 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\
+	  & \textit{Dielectric constants} & \\
+ 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
+ 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\
+
+		\hline  	
+	\end{tabular}
+	\label{table1}
+\end{table}
+
 \end{document}

### 2020-04-23 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 \subsection{General}
+
+We study elastodynamic waves propagating through an elastic isotropic, homogeneous steel plate.
+Using an electro-mechanical piezocomposite actuator, deliver impulsive sources on to the top surface of the steel specimen.
+On the bottom, an array of 13 piezoelectric (lead zirconate titanate, PZT) transducers are mounted in an aluminium array holder.
+The aim of this study is to better understand the force produced by the piezoelectric actuator by studying the waves produced at different locations on the bottom of the specimen.
+
+Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame.
+Small rummer pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame.
+Centrally located on the top surface is a piezoelectric actuator build in house (details in Section XX).
+This sensor is connected to an high-voltage pulsing unit (HVP, Elsys Instruments AE-HV-MUX).
+This unit consist of a PiezosystemJena voltage amplifier for pulse generation (HVP 1000/200) that is fully integrated with the data acquisition (DAQ) software (Elsys Instruments TraNET).
+Figure \ref{fig1}(c) shows the circuit diagram of the HPV that is used to deliver an amplified voltage pulse to the piezoelectric actuator.
+The pulse and discharge of the system is depicted in the Figure \ref{fig1}(d).
+The time-dependent change in voltage when the switch position is in ``pulse'' (state 1) is given as:
+
+\begin{equation}
+\begin{array}{lcc}
+  V(t) =  V_{0} \cdot \left[ 1 - exp\left(\frac{t}{R_{1}\cdot C_{PZT}} \right) \right], & \text{for} & 0 < t \leq t_{0}\\
+\end{array}
+\label{eq1}
+\end{equation}
+
+\noindent where $C_{PZT}$ = 300 pF, $R_{1}$ = 5 $\Omega$, $V_{0}$ = 200 V and the time of the pulse was set to $t_{0}$ = 1 $\mu$s.
+Discharging the systems required the switch to move to position 2 and we can solve for the theoretical discharge voltage:
+
+\begin{equation}
+\begin{array}{lclcc}
+  V(t) =  V_{0} \cdot exp\left(-\frac{t - t_{0}}{R_{2}\cdot C_{eq}}\right), & \text{for} & t > t_{0}\\
+\end{array}
+\label{eq2}
+\end{equation}
+
+\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatics.
 

### 2020-04-28 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 Small rummer pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame.
-Centrally located on the top surface is a piezoelectric actuator build in house (details in Section XX).
+Material properties of the steel plate required to model the wave propagation problem in the steel plate are given in Table \ref{table1}.
+Centrally located on the top surface is a piezoelectric actuator built in-house.
 This sensor is connected to an high-voltage pulsing unit (HVP, Elsys Instruments AE-HV-MUX).
@@
 
-\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatics.
+\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatic theory.
+Figure \ref{fig1}(b) show the array holder for the passive sensor (KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source.
+The aluminium array had a 7 $\time$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.
+In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e.
+aligned in the $3$-direction) and, therefore, have focused most of our sensors converge to one quadrant.
+Similar colors of the sensors locations in Figure \ref{fig1}(b), represents similar epicentral locations.
+We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and have shown that there appear to be little to no directivity in the active source.
+
+A total of 13 sensor are used and the spectral characteristics of these sensors have been well examined in the literature using the absolute calibration methods \citep{Glaser1998, McLaskey2010, McLaskey2012, Selvadurai2015, Selvadurai2019, Wu2020}.
+\citet{Glaser1998} provides a detailed account to sensor attributes used by KRN Services, including a the small field emission transistor (FET)-based Sanyo (2SK715W) preamplifier internal to the sensor casing to improve impedance matching.
+These sensors have shown flat displacements-responses between 100 kHz to 1 MHz \citep{McLaskey2012, Selvadurai2019}.
+At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more like accelerometer \citep{Wu2020}.
 
@@
 \includegraphics[scale= 1.0]{FIG1.pdf} 
-\caption{\textbf{(a)}  }
+\caption{\textbf{(a)} General schematic of the calibration station located in the Rock Physics and Mechanics Laboratory at ETH Zurich.
+We used apparatus to apply an active source downwards, which was centrally located on the top of a steel platen.
+This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors.
+\textbf{(b)} The array of PZT sensors are shown where the colors indicate their epicentral location with respect to the source and is used throughout the study.
+\textbf{(c)} Driver circuit for pulse source diagram showing the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX).
+\textbf{(d)} The solution for the time-dependent pulse and discharge of the voltage applied across the PZT element using circuit theory.
+}
 	\label{fig1} 
 \end{figure}
-
-\begin{figure}[ht]
-     	\centering
-\includegraphics[scale= 1.0]{FIG2.pdf} 
-\caption{\textbf{(a)}  }
-	\label{fig2} 
-\end{figure}
-
-\subsection{Material properties}
 
@@
 
-\subsection{Elsys Instruments High-voltage Multiplexer}
-***need information on \textbf{Piezosystem Jena HVP1000/100MODext.} from Roman Bertschi***
+\subsection{Lamb's problem and PZT actuators}
+
+The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1988}.
+More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space.
+These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology.
+These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g.
+ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.).
+We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method.
+This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.
+
+While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
+In Figure \ref{fig2}(a) we show cross-section A-A from Figure \ref{fig1}(b).
+The source is produced by the piezoelectric actuator on the top surface of the steel plate causing elastodynamic spherical stress waves (colored) to propagate outwards.
+This wave-field is actually only used as a reference and is not representative of the source produced from the PZT actuator (determined later).
+The colored region in Figure \ref{fig2}(a) represents the velocity wave-field produced from a ball drop at the actuator location, which has been well-studied in recent years \citet{McLaskey2010, Wu2018, Wu2020}.
+In Figure \ref{fig2}(a), we show the ``toolchain'' that is used to process the seismic waves produced by the PZT actuator.
+The PZT actuator is used to produce a force $f_{j}\left( \mathbf{\xi}, \tau \right)$ on the top surface at a point $\mathbf{\xi}$ of the steel platen.
+A passive sensor, on the bottom surface at point $\mathbf{x}$, attempts to measure the theoretical displacements with time $u_{k}\left( \mathbf{x}, t \right)$.
+Green’s functions are a basic ingredient in the Knopoff--de Hoop representation theorem \citep{Burridge1964} is the solution to the elastic wave equation relating the elastic displacements to the source throughout he elastic half-space.
+Unfortunately, the passive sensors are unable to truly capture the theoretical displacements and will distort the measured signal $s(t)$ according to its instrument response $i_{k}(t)$.
+In this study we consider the instrument response to include effects of the sensor, cabling and internal component of the data acquisition allowing for digitization of the signal.
+
+\begin{figure}[h]
+     	\centering
+\includegraphics[scale= 1.0]{FIG2.pdf} 
+\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function.
+The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}.
+P and S waves are highlighted for reference only.
+The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
+	\label{fig2} 
+\end{figure}
+
+Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, developing more understanding of realistic force-time function produced by the PZT actuators has many potential benefits.
+The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
+To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources.
+We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.
+By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty.
+We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
 
@@
 
-Using the classical theory describing dynamic elasticity \citep{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$, which is given as the convolution of the force with the Green's function
+Using the classical theory describing dynamic elasticity, summarize by \citet{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$, which is given as the convolution of the force with the Green's function
 
@@
 \noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.
+For the elastodynamic solutions studies here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI, as mentioned above).
 The true Green's function describes the displacement at time $t$ and location $\mathbf{x}$ for the unit impulse force at location $\mathbf{\xi}$ at the delayed time $\tau$.
@@
 
-Our study aims at determining the nature of the source produced that occurs we use the PZT crystal as active source. WE first decompose the source into two parts as shown here:
+Our study aims at determining the nature of the source produced that occurs we use the PZT crystal as active source. We first decompose the source into two parts as shown here:
 

### 2020-04-28 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
-In Figure \ref{fig2}(a) we show cross-section A-A from Figure \ref{fig1}(b).
-The source is produced by the piezoelectric actuator on the top surface of the steel plate causing elastodynamic spherical stress waves (colored) to propagate outwards.
-This wave-field is actually only used as a reference and is not representative of the source produced from the PZT actuator (determined later).
-The colored region in Figure \ref{fig2}(a) represents the velocity wave-field produced from a ball drop at the actuator location, which has been well-studied in recent years \citet{McLaskey2010, Wu2018, Wu2020}.
+In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b).
+The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Figure \ref{fig1}.
+The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards.
+In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later).
+For this example, we show the velocity wave-field produced from a ball drop at the same location as the PZT actuator location from numerical finite element simulations in ABAQUS.
+
+The type of source creating the stress waves is important.
+\citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes.
+He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive, noting that each type is imperfect and has its trade offs.
+In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g.
+trixaial pressure cell).
+To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.
+
 In Figure \ref{fig2}(a), we show the ``toolchain'' that is used to process the seismic waves produced by the PZT actuator.
@@
 \label{theo}
+
 We review the methodology that will model the forces produced by an active source piezoelectric transducer.

### 2020-04-29 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 \usepackage[utf8]{inputenc}
+\usepackage{mathrsfs}
 
@@
 \begin{keyword}
-Acoustic emissions, absolutely calibrated sensors, active source time function, empirical Green's functions
+Acoustic emissions, physical acoustics, non-destructive testing, active source methods
 \end{keyword}
@@
 The premise is to use well-understood physics associated with wave propagation, in fluids or solids media, to probe properties and assess its state in a non-destructive manner.
+
+\\\
+
+The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
+To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources.
+We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.
+By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty.
+We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
 
@@
 In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later).
-For this example, we show the velocity wave-field produced from a ball drop at the same location as the PZT actuator location from numerical finite element simulations in ABAQUS.
+For this example, a snapshot of the velocity wave-field, produced from a capillary fracture is shown from numerical finite element simulations in ABAQUS \citep[adapted from fig.
+2][]{Selvadurai2019}.
 
-The type of source creating the stress waves is important.
+Properties of the source creating the stress waves is important.
 \citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes.
@@
 
-In Figure \ref{fig2}(a), we show the ``toolchain'' that is used to process the seismic waves produced by the PZT actuator.
-The PZT actuator is used to produce a force $f_{j}\left( \mathbf{\xi}, \tau \right)$ on the top surface at a point $\mathbf{\xi}$ of the steel platen.
-A passive sensor, on the bottom surface at point $\mathbf{x}$, attempts to measure the theoretical displacements with time $u_{k}\left( \mathbf{x}, t \right)$.
-Green’s functions are a basic ingredient in the Knopoff--de Hoop representation theorem \citep{Burridge1964} is the solution to the elastic wave equation relating the elastic displacements to the source throughout he elastic half-space.
-Unfortunately, the passive sensors are unable to truly capture the theoretical displacements and will distort the measured signal $s(t)$ according to its instrument response $i_{k}(t)$.
-In this study we consider the instrument response to include effects of the sensor, cabling and internal component of the data acquisition allowing for digitization of the signal.
+In Figure \ref{fig2}(a), we show the five components of ``toolchain'' that is used to link the source to the measured signal.
+The PZT actuator is used to produce a (\textit{1}) \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$.
+Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be computed using the (\textit{2}) \textbf{Green's function} $G_{kj}$.
+The Green's functions map the (\textit{3})\textbf{ elastic displacements} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$.
+A passive sensor, on the bottom surface at point $\mathbf{x}$ and attempts to measure the theoretical displacements $u_{k}$.
+Unfortunately, the passive sensors always will distort the (\textit{4}) \textbf{measured signal}  $s$ according to its (\textit{5}) \textbf{instrument response} $i_{k}$ at position $\mathbf{x}$ and time $t$.
+
+developing more understanding of realistic force-time function produced by the PZT actuators has many potential benefits.
+Due to these properties we are able simply study and isolate individual components of the ``toolchain''.
 
@@
 
-Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, developing more understanding of realistic force-time function produced by the PZT actuators has many potential benefits.
-The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
-To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources.
-We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.
-By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty.
-We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
-
-\section{Theory}
+\section{Theoretical Framework}
 \label{theo}
 
-We review the methodology that will model the forces produced by an active source piezoelectric transducer.
-This methodology takes advantage of the theory surrounding elastodynamic wave propagation in an elastic medium.
 We build on the recent studies of signal analysis and instrument calibration by \citet{McLaksey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}.
-We assume that wave propagation can be adequately described by convolution with the Green's function and that each component in our analysis can be modeled as a linear-time invariant system.
-We are assuming that changes in the sensor and source behavior and material properties are unaffected over time.
-We assume point representations of both the sensor and source location.
-This so-called ``aperture'' effect is minimized by using the point contact conical PZT crystal but some deviations might be incurred.
+Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our system in a linear time-invariant (LTI) fashion.
+This assumes that changes in the sensor and source behavior and material properties are unaffected over time.
+We assume point representations of both the sensor and source location, which might be influenced so-called ``aperture'' effect.
+However, this is minimized by using the point contact conical PZT crystal, which will be discussed later when we examine in more detail how the force systems of passive and active PZT sensors.
 
-Using the classical theory describing dynamic elasticity, summarize by \citet{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$, which is given as the convolution of the force with the Green's function
+Using the classical theory describing dynamic elasticity \citep{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$.
+This is given as the convolution of the force with the Green's function
 
@@
 \end{equation}
-
 \noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.
-For the elastodynamic solutions studies here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI, as mentioned above).
-The true Green's function describes the displacement at time $t$ and location $\mathbf{x}$ for the unit impulse force at location $\mathbf{\xi}$ at the delayed time $\tau$.
+For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties.
+The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ or the identity convolution.
 
@@
 We can relate the true surface displacement $u_{k}$ to voltage measurement $s$ using the instrument response, which is given as
-
    \begin{equation}
@@
         s\left( \mathbf{x}, t \right) =
-            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(t \right).
+            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(\mathbf{x},t \right).
     \end{equation}
-
     \noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the forces which produced them:
@@
         s\left( \mathbf{x}, t \right) =
-            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(t \right) =  
+            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(\mathbf{x}, t \right) =  
                 f_{j}\left( \mathbf{\xi}, \tau \right) \ast 
-                g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right) \ast i_{k}\left( t \right).
+                g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right) \ast i_{k}\left(\mathbf{x},  t \right).
     \end{equation}
@@
 
-Our study aims at determining the nature of the source produced that occurs we use the PZT crystal as active source. We first decompose the source into two parts as shown here:
+\subsection{Time domain characteristics of the Force Function}
+\label{force_time}
+
+Our study aims at determining the nature of the dynamic transient source produced from the PZT actuator. We first decompose the source into two parts as shown here:
 
@@
     \label{eq4}
-    f_{j}\left( \mathbf{\xi}, \tau \right) = f^{*}_{j}\left( \mathbf{\xi}, \tau \right)  \ast \kappa \left( \tau \right),
+    f_{j}\left( \mathbf{\xi}, \tau \right) =A_{0} \cdot f^{*}_{j}\left( \mathbf{\xi}, \tau \right) ,
 \end{equation}
@@
 \noindent where $f^{*}_{j}$ is the normalized force-time function that has units (N) and a general shape to that follows the electro-mechanical behavior of the coupled high-voltage discharge and sensor systems.
-A unitless scaling factor $\kappa$ will be used to scale the normalized force time-function $f^{*}$ to the true force-time function $f$ and likely varies with the time as the electrical pulse is applied to the active source.
+A unitless scaling factor $\kappa(\tau)$ will be used to scale the normalized force time-function $f^{*}$ to the true force-time function $f$ and likely varies with the time as the electrical pulse is applied to the active source.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 0.9]{FIG2b.pdf} 
+\caption{\textbf{(a)} Enhanced view of the contact region from the concial PZT actuator.
+\textbf{(b)} Simplified schematic showing the electro-mechanical systems and the estimate region where a pressure pulse $p_{j}$ (red) is generated when excited by the impulsive voltage.
+We assume that the force-time $f_{j}$ (blue arrow) is simply the integration of transient pressure over a constant circular contact area $A_{contact}$ and acting only in the 3-direction.
+\textbf{(c)} Model summarizing the complex behavior of the PZT actuator (both internal and external) using an under-damped spring-mass damper systems whose behavior follow equation \eqref{eq4b}.
+\textbf{(d)} The normalized force-time function for: $A_{0}$ = 1 N, $\Gamma$ = 0 MHz and $\Lambda$ = 4.7 MHz (black line) and $A_{0}$ = 1 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz (blue line).}
+	\label{fig2b} 
+\end{figure}
+
+In Figure \ref{fig2b}(a) we look in detail at the position where the PZT actuator contacts steel plate.
+The actuator has threads on its body and is loaded on the plate by applying a small torque where the conical PZT tip is loaded through a thin layer of nickel (0.03 mm thick).
+This nickel foil is the cathode of the electro-mechanical circuit shown in Figure \ref{fig2b}(b), which represent a more detailed representation of the PZT actuator mentioned in the driver circuit (see Figure \ref{fig1}(c)).
+A small amount of contact gel is used to improve contact between the nickel cathode and steel plate but nickel was chosen due to is malleability and it formed a strong contact with the steel platen under minimal pressure \citep{Glaser1998}.
+To better understand the transient point force $f_{j}$ applied, we consulted literature in the biomedical industry that has studied piezomaterial, with similar pulsed excitation voltages, to perform ultrasonic reconstruction in acoustic media.
+\citet{Christensen1988} looked at the pressure caused by a an electrical circuit that generated a sharp voltage pulse similar to that shown in Figure \ref{fig1}(d).
+Since the propagate waves through an acoustic medium they are interested in the time-dependent pressure boundary condition $p_{j}(\tau)$.
+To convert from pressure (over the tip area of the conical PZT) to an equivalent force $f_{j}$ we assume that the transient pressure field produced was uniform and therefore integrate over the contact tip area $A_{contact} = \pi r_{contact}^{2}$.
+For this PZT sensor the conical crystal has a contact radius of $r_{contact} = $ 0.75 mm.
+\cite{Christensen1988} found that the transient response of the pressure did not precisely duplicate the waveform of the voltage (see Figure \ref{fig1}(b)) due to the resonant properties of the crystal.
+When excited by a impulsive source, the crystal will resonate sinusoidal at its fundamental frequency and the wave will decay based in internal, external and transmitted losses.
+The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped spring-mass damper system shown in Figure \ref{fig2b](c).
+\citet{Breckenridge1990} also showed evidence of under-damped behavior when exciting a conical PZT on an aluminium plate.
+
+\citet{Christensen1988} notes that the damping of the pressure will be inversely proportional to the mechanical loss factor of the PZT crystal, but we argue that more variables might be contributing to this of the coupling of all the internal component such as the backing mass material and shape, they connections between the internal electrically conductive components, the shape of the crystal, the type of potting agent, the amount of coupling gel used, the type of material being pulsed (fluid or elastic), amongst other features \citep{Glaser1998}.
+We argue that attempting to solve the full systems behavior with all these complexities is counter productive to the crux of this study.
+By the properties of convolution describing the wave propagation in equations \eqref{eq1}, we can assume that the measured signals will still have the general shape of the normalized force-time $f^{*}$ embedded in the measurements.
+We generalized the normalized force time function shown in Figure \ref{fig2b}(d) as follows
+
+\begin{equation}
+    \label{eq4b}
+   f(t) = A_{0} \cdot exp[- \Gamma \cdot t]\cdot sin(\Lambda\cdot t) ,
+\end{equation}
+
+\noindent where $A_{0}$ = 1 N for the normalized case, $\Gamma$ and $\Lambda$ are the decay and vibration parameters of the normalized force-time function.
+We note that the subscript $_{j}$ has disappears since we are assuming that the normalized force is acting only in the $`3'$-direction.
+Later, we will describe how these two parameters are used in an inversion to minimize the errors between the theoretical displacements $u_{k}$ and measured signals $s$ over all the measured sensors.
+For the case in Figure \ref{fig2b}(d), $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, which represented the best-fit solution for our analysis of the specific PZT used in this study following the excitation pulse in Figure \ref{fig1}(d).
+
+\subsection{Calculating the Instrument Response}
 
@@
 \noindent where $I_{k}$, $S$, $F_{j}$ and $G_{kj}$ are calculated from the temporal Fourier transforms of the $i_{k}$, $s$, $f_{j}$ and $g_{kj}$, respectively.
-As we will see in Section \ref{XXX}, instrument responses was calculated for the sensor array shown in Figure \ref{fig1}, where a controlled force-time function were applied at the central location by dropping small steel balls of different diameters onto the surface from a known height.
+In a concerted study, we have predetermined the instrument responses for the exact same sensor configuration shown in Figure \ref{fig1}.
+However, \citet{Wu2020} produced a known force-time function by dropping small steel balls of different diameters onto the surface from a known height at the identical location that will be used for the PZT actuator later.
 According to Hertzian contact theory, it is possible to assume a source time function that is a function of the material properties of the ball and steel platen ($E, \nu, \rho$), the radius of ball, and the drop height.
-This method has been popularized over the recent years due to a highly reliable and repeatable force-time function $f$ produced from ball impact and the ability to absolutely calibrate the acoustic emission sensors over a wide spectral range \citep{McLaskey2010, McLaskey2012, McLaskey2015}.
+This method has been popularized over the recent years due to a highly reliable and repeatable force-time function $f$ produced from ball impact and the ability to absolutely calibrate the acoustic emission sensors over a wide spectral range \citep{Breckenridge1990, McLaskey2010, McLaskey2012, McLaskey2015}.
 
-We will use the known instrument response to better understand the source produced from the active PZT transducer.
-We can rearrange equation \eqref{eq5} to obtain the true force in the frequency domain:
+For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu2020} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm.
+The balls had elastic modulii of $E_{ball}$ = 210 GPa and Poisson ratio of $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}.
+Once the force-time function is know, we use equation \eqref{eq5}, now with $F_{ball}\left( \mathbf{\xi}, \hat{\omega} \right)$, which represents the Fourier transform of the ball drop, to calculate the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.
+Calculating the lower frequency instrument response (i.e.
+1 kHz to 50 kHz ) is not straightforward and the readers should also consult \citet{Wu2018} for a summary of methods.
+Figure \ref{fig6}(a) shows the full instrument response for all the passive sensors shown in Figure \ref{fig1}(b).
+The color coding related to the sensors epicentral distance from the ball drop source.
+In this study, we are only interested in the higher frequency (100 kHz to 1 MHz) sensor behavior for the reconstruction of the PZT actuator force time function.
+This range is shown in Figure \ref{fig6}(b).
+We see that the instrument response is insensitive to the take-off angle.
+This is important to the analysis and will be addressed in the more detail later.
+This insensitivity has also been acknowledged in the past for the same KRNPC-BB conical-style sensors used here \citep{Goodfellow2015, Selvadurai2019}.
+Results from this calibration campaign are summarized and more details have been given in \citet{Wu2020}.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 1.0]{FIG6.pdf} 
+\caption{Summary of the calibration experiments performed by \citet{Wu2020} to determine the instrument response for ball drops, performed \textit{a priori}, in the same location as where our PZT actuator was later placed.
+\textbf{(a)} The full range of calibrated frequencies (1 kHz to 1 MHz) is shown.
+\textbf{(b)} For our study, we only consider high-frequency aspect and therefore will only use the instrument responses between components 100 kHz to 1 MHz.
+Colors are indicative of the sensors location as defined in Figure \ref{fig1}(b).
+For all the details please consult \citet{Wu2020}.
+}
+	\label{fig6} 
+\end{figure}
+
+\subsection{Spectral Deconvolution of the Problem}
+
+Having the specific broadband instrument response, solved using the well-understood ball drop source for our exact sensor-source layout, is paramount to accurately model the force-time function of the PZT actuator described by equation \eqref{eq4b}.
+If we now consider the original problem in Figure \ref{fig2}, we can start with the recorded signal produced from the PZT actuator and use the instrument response to determined the mechanical vibration.
+In the Fourier domain, we can rearrange the left hand side of equation \eqref{eq3} to estimate the spectral response of the theoretical vibration $U_{k}(\mathbf{x},t)$ caused by the transient PZT actuator:
 
@@
 \begin{split}
-F_{j}\left( \mathbf{\xi}, \hat{\omega} \right) & = 
-        S\left( \mathbf{x}, \omega \right) \cdot \left[ I_{k}\left(\omega \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1}, \\
+U_{k}\left( \mathbf{x}, \omega \right) & = 
+        \frac{S\left( \mathbf{x}, \omega \right) }{ I_{k}\left( \mathbf{x},\omega \right)}.
 \end{split}
@@
 
-\noindent where by combing the Fourier transform of equation \eqref{eq4} we obtain an expression for the normalized force-time function,
+Approaching the problem from the source side (right hand side of equation \eqref{eq3}), we can also estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is shown as:
 
 \begin{equation}
-    \label{eq7}
+    \label{eq6a}
 \begin{split}
-F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right) & = 
-        S\left( \mathbf{x}, \omega \right) \cdot \left[ K\left(\hat{\omega}\right) \cdot I_{k}\left(\omega \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1}.\\
+U_{k}\left( \mathbf{x}, \omega \right) & = 
+       F_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right).
 \end{split}
@@
 
-\noindent To solve the features about $F^{*}_{j}$, we will need to \textit{a priori} knowledge of sensors instrument response, also needed will be signal measurements $S$ and the true Green's function $G_{kj}$ but we will still not know the frequency-dependent scaling function $K(\hat{\omega})$ -- a primary calculation that is required to obtain the true force-time function produced by the active PZT transducer.
+\noindent Substituting the Fourier transform of the force-time function describe in equation \eqef{eq4}, we obtain
+
+\begin{equation}
+    \label{eq6b}
+\begin{split}
+U_{k}\left( \mathbf{x}, \omega \right) & = 
+       A_{0}\cdot \delta (\omega)\cdot F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right),
+\end{split}
+\end{equation}
+
+\noindent where the Fourier transform of the scaling parameter is $\mathcal{F}[A_{0}] = A_{0}\cdot\delta(\omega)$ and $\delta$ is the Dirac delta function.
+Next we can combine equations \eqref{eq6} and \eqref{eq6b} to solve for the scaling factor for the force-time function $A_{0}$:
+
+\begin{equation}
+    \label{eq6b}
+\begin{split}
+A_{0} = \mathcal{F} ^{-1}[A_{0}\cdot \delta (\omega)] & = \frac{S\left( \mathbf{x}, \omega \right) } 
+{ I_{k}\left( \mathbf{x},\omega \right)\cdot F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right)},
+\end{split}
+\end{equation}
+
+\noindent where $\mathcal{F}^{-1}[\cdot]$  is the inverse Fourier transform.
+We see that all of the components on the right hand side can be measured ($S$) or calculated ($G_{kj}$) or have been determined \textit{a priori} ($I_{k}$) .
+We must assume that $A_{0}$ is constant over time and and the force-time function $f(\mathbf{\xi}, \tau)$, in equation \eqref{eq4b}, accurately captures the force released during the impulsive excitation of the PZT actuator.
 
@@
 Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
-Figure \ref{fig3}(b) shows the empirical Green's functions (EGF) at a give epicentral location from the source.
+Figure \ref{fig3}(b) shows the Green's functions (EGF) at a give epicentral location from the source.
 We call this the empirical Green's function since it is a numerical approximation of the true Green's function that is the resulting ground displacements $u$ at point $\mathbf{x}$ from a unit impulse function $\delta_{j}(\mathbf{\xi}, \tau)$.
@@
 \includegraphics[scale= 1.0]{FIG3.pdf} 
-\caption{\textbf{(a)} Measurements on from passive PZT transducers from a source produced from the active sensor.
-The color scheme represents sensors at the different epicentral locations shown in Figure \ref{fig1}(b).
-\textbf{(b)} Green's function solutions using generalized ray theory for a semi-infinite elastic, homogeneous steel platen at different epicentral locations.
-The empirical Green's function (EGF) is equal to the true Green's function represents the displacements produced from the unit impulse force $\delta_{j}(\tau)$.
+\caption{\textbf{(a)} Measurements the array of passive PZT transducers from a PZT actuator source described in Figure \ref{fig1}(d).
+The color scheme represents the different epicentral locations of each sensor in Figure \ref{fig1}(b).
+\textbf{(b)} Green's function solutions using generalized ray theory for a semi-infinite elastic, homogeneous steel plate at different epicentral locations.
+The empirical Green's function (EGF) is the numerical estimate of the true Green's function, which is displacements produced from the unit impulse force $\delta_{j}(\mathbf{\xi}, \tau)$.
 We see the various phase arrival predicted from the model.}
@@
 Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.
-We show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) from the epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively.
+For clarity, we only show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) from the epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively.
 We see that the sensors appear to capture the multiple phase arrivals and this is believed to be due to the conical nature of the PZT crystal and its ability to capture wave arrivals at high azimuthal incident angles \citep{Selvadurai2019}.
@@
 
-\textbf{**Use Christensen (1988) to better define the force-time function**} We created the normalized force-time function based on characteristic of the first arrival P wave.
+ We created the normalized force-time function based on characteristic of the first arrival P wave.
 In Figure \ref{fig5}(c) we show the methodology for generating $f^{*}_{j}$.
@@
 
-\begin{figure}[ht]
-     	\centering
-\includegraphics[scale= 0.9]{FIG5b.pdf} 
-\caption{\textbf{(a)}  }
-	\label{fig6} 
-\end{figure}
-
 To solve for the scaling function $K(\hat{\omega})$ we need to know the instrument response function $i(t)$.
@@
 Figure \ref{fig6}(b) focuses only on the results for frequencies between $f$ = 100 kHz to 1000 kHz, which is more important to our understanding of the true force-time function in our case.
-
-\begin{figure}[ht]
-     	\centering
-\includegraphics[scale= 0.9]{FIG6.pdf} 
-\caption{\textbf{(a)}  }
-	\label{fig6} 
-\end{figure}
 

### 2020-04-29 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 \end{equation}
+
 \noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.
@@
     \end{equation}
+
     \noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the forces which produced them:
@@
 
-\noindent where $A_{0}$ = 1 N for the normalized case, $\Gamma$ and $\Lambda$ are the decay and vibration parameters of the normalized force-time function.
+\noindent where $A_{0}$ is the scaling factor (= 1 N for the normalized case), $\Gamma$ and $\Lambda$ are the decay and vibration parameters of the normalized force-time function.
 We note that the subscript $_{j}$ has disappears since we are assuming that the normalized force is acting only in the $`3'$-direction.
@@
         I_{k}\left(\omega \right) = 
-        S\left( \mathbf{x}, \omega \right) \cdot \left[ F_{j}\left( \mathbf{\xi}, \hat{\omega} \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1} .
+        S\left( \mathbf{x}, \omega \right) \cdot \left[ F_{j}\left( \mathbf{\xi}, \omega \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \omega \right)\right]^{-1} .
 \end{equation}
@@
 For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu2020} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm.
-The balls had elastic modulii of $E_{ball}$ = 210 GPa and Poisson ratio of $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}.
-Once the force-time function is know, we use equation \eqref{eq5}, now with $F_{ball}\left( \mathbf{\xi}, \hat{\omega} \right)$, which represents the Fourier transform of the ball drop, to calculate the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.
+The balls had elastic modulii $E_{ball}$ = 210 GPa and Poisson ratio $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}.
+Once the force-time function is know, we use equation \eqref{eq5}, now with $F_{ball}\left( \mathbf{\xi}, \omega \right)$, which represents the Fourier transform of the ball drop, to calculate the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.
 Calculating the lower frequency instrument response (i.e.
@@
 \subsection{Spectral Deconvolution of the Problem}
-
+\label{Spec_deconv}
 Having the specific broadband instrument response, solved using the well-understood ball drop source for our exact sensor-source layout, is paramount to accurately model the force-time function of the PZT actuator described by equation \eqref{eq4b}.
@@
 
-Approaching the problem from the source side (right hand side of equation \eqref{eq3}), we can also estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is shown as:
+Approaching the problem from the source side (right hand side of equation \eqref{eq3}), we can estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is shown as:
 
@@
 U_{k}\left( \mathbf{x}, \omega \right) & = 
-       F_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right).
+       F_{j}\left( \mathbf{\xi}, \omega \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \omega\right).
 \end{split}
@@
 U_{k}\left( \mathbf{x}, \omega \right) & = 
-       A_{0}\cdot \delta (\omega)\cdot F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right),
+       A_{0}\cdot \delta (\omega)\cdot F^{*}_{j}\left( \mathbf{\xi}, \omega \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \omega\right),
 \end{split}
@@
 
-\noindent where the Fourier transform of the scaling parameter is $\mathcal{F}[A_{0}] = A_{0}\cdot\delta(\omega)$ and $\delta$ is the Dirac delta function.
+\noindent where the Fourier transform of the force-time magnitude parameter is $\mathcal{F}[A_{0}] = A_{0}\cdot\delta(\omega)$ and $\delta$ is the Dirac delta function.
 Next we can combine equations \eqref{eq6} and \eqref{eq6b} to solve for the scaling factor for the force-time function $A_{0}$:
@@
 \begin{equation}
-    \label{eq6b}
+    \label{eq6c}
 \begin{split}
-A_{0} = \mathcal{F} ^{-1}[A_{0}\cdot \delta (\omega)] & = \frac{S\left( \mathbf{x}, \omega \right) } 
-{ I_{k}\left( \mathbf{x},\omega \right)\cdot F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right)},
+ F_{j}\left( \mathbf{\xi}, \omega \right) = A_{0}\cdot \delta (\omega)  \cdot F^{*}_{j}\left( \mathbf{\xi}, \omega \right) & 
+=\left[ \frac{S\left( \mathbf{x}, \omega \right) } 
+{ I_{k}\left( \mathbf{x},\omega \right)} \right]
+\left[ \frac{1}{ G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \omega\right)} \right].
 \end{split}
@@
 
-\noindent where $\mathcal{F}^{-1}[\cdot]$  is the inverse Fourier transform.
-We see that all of the components on the right hand side can be measured ($S$) or calculated ($G_{kj}$) or have been determined \textit{a priori} ($I_{k}$) .
-We must assume that $A_{0}$ is constant over time and and the force-time function $f(\mathbf{\xi}, \tau)$, in equation \eqref{eq4b}, accurately captures the force released during the impulsive excitation of the PZT actuator.
+\noindent We see that all of the components on the right hand side can be measured ($S$), can be calculated ($G_{kj}$) or have been determined \textit{a priori} ($I_{k}$) .
+In this approach we assume that $A_{0}$ is constant over time and and the force-time function $f(\mathbf{\xi}, \tau)$ described accurately by equation \eqref{eq4b}.
 
@@
 \label{results}
-
-In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b).
-Waveforms have been color coded following Figure \ref{fig1}(b) to show measurements taken at similar epicentral distances.
-These waveform we produced by actively exciting the source sensor located at the top central location of the steel platen.
-For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen.
-This allows us to analyze the wave using the approximation that the plate is in fact semi-infinite.
+\subsection{Time domain analysis}
+A total of 1000 pulses of the PZT actuator were performed but for our results we show a single pulse to show the methodology that follows equations \eqref{eq1} to \eqref{eq6b}.
+The source was highly repeatable in at the high-frequencies we investigated.
+From the 1000 tests, the average  Pearson correlation coefficient from the stacked mean was $R$ = \textbf{0.95}.
+In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b) for a random pulse with color indicating different epicentral distances.
+For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen that would occur if longer signals were analyzed.
+The sampling rate was $F_{s}$ = 20 MHz making each trace 1000 samples.
+Since boundary reflections are not considered, we can approximate that the plate is in fact semi-infinite.
 Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
-Figure \ref{fig3}(b) shows the Green's functions (EGF) at a give epicentral location from the source.
-We call this the empirical Green's function since it is a numerical approximation of the true Green's function that is the resulting ground displacements $u$ at point $\mathbf{x}$ from a unit impulse function $\delta_{j}(\mathbf{\xi}, \tau)$.
-In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) for the numerical models.
+Figure \ref{fig3}(b) shows the Green's functions at different epicentral locations, moving out from the source at $x$ = 0 mm.
+We call these approximations the empirical Green's function (EGF) since it is a numerical approximation of the true Green's function.
+The true Green's function can be calculated by replacing the force-time function in equatoin \eqref{eq1} with the a unit impulse (Dirac delta) function $\delta_{j}(\mathbf{\xi}, \tau)$.
+In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) from the numerical models.
 
@@
 \includegraphics[scale= 1.0]{FIG3.pdf} 
-\caption{\textbf{(a)} Measurements the array of passive PZT transducers from a PZT actuator source described in Figure \ref{fig1}(d).
+\caption{\textbf{(a)} Measurements taken from the passive PZT transducers from a single transient PZT excitation described in Figure \ref{fig1}(d).
 The color scheme represents the different epicentral locations of each sensor in Figure \ref{fig1}(b).
-\textbf{(b)} Green's function solutions using generalized ray theory for a semi-infinite elastic, homogeneous steel plate at different epicentral locations.
-The empirical Green's function (EGF) is the numerical estimate of the true Green's function, which is displacements produced from the unit impulse force $\delta_{j}(\mathbf{\xi}, \tau)$.
+\textbf{(b)} Green's function solutions determined using generalized ray theory for a semi-infinite elastic, homogeneous steel plate at different epicentral locations.
 We see the various phase arrival predicted from the model.}
@@
 Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.
-For clarity, we only show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) from the epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively.
-We see that the sensors appear to capture the multiple phase arrivals and this is believed to be due to the conical nature of the PZT crystal and its ability to capture wave arrivals at high azimuthal incident angles \citep{Selvadurai2019}.
-Results in Figure \ref{fig4} are representative of the measurements across all 13 passive sensors.
+For clarity, we only show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) at epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively.
+We see that the sensors captures various phase arrivals predicted form the model.
+The ability of these sensors to accurately capture wave arrivals and information even at high azimuthal incident angles has been discussed in the literature \citep{Goodfellow2015, Selvadurai2019} and is due to the conical geometry of the PZT crystal.
 
@@
 
-To best show the approach we take to solve for the force time function produced by the active source, we focus on the measurements taken from sensors A3 at epicentral distance $x$ = 46 mm.
-Figure \ref{fig5}(a) shows the measurements and EGFs.
-We focus on detail B, which looks at the first arrival P wave.
-In Figure \ref{fig5}(b) this is shown in more detail with the sensors (green trace) and EGF (black trace) clearly visible.
-Since we know that, in the time domain, the signal produced on the sensors the force-time function are convolved with the associated Green's function, the shape of the specific wave with be representative of the source.
-The blue curve in Figure \ref{fig5}(b) is a best-guess approximation of the source and will be use to estimate the general normalized force-time function $f^{*}_{j}$ from equation \eqref{eq4}.
+We further focus on the measurements taken from sensors A3 at epicentral distance $x$ = 46 mm.
+Figure \ref{fig5}(a) shows the measurements (green) and EGF (black line).
+Detail B in Figure \ref{fig5}(b) focuses on the first arrival P wave.
+As discussed in Section \ref{force_time}, the measured waveforms will display features of the source due to the convolution operations in equations \eqref{eq1} to \eqref{eq3}.
+In Detail B we superimpose the normalized force-time function $f^{*}$ from Figure \ref{fig2b}(d) for reference.
+We see that there appears to be some similarities in our measured signals that would justify our hypothesized force-time function given in equation \eqref{eq4b}.
+While the fit is not perfect -- the signal sensor A3 appears to a lower decay parameter $\Gamma$ -- this will be addressed when we simultaneously invert to match these variables on all sensors.
+Before doing so, we must calculate the scaling factor in the frequency domain using equation \eqref{eq6c}.
 
@@
 
- We created the normalized force-time function based on characteristic of the first arrival P wave.
-In Figure \ref{fig5}(c) we show the methodology for generating $f^{*}_{j}$.
-We based this on the technical specifications of the high-voltage pulsing unit described in Section \ref{XXX}.
-In this experiment we applied a 100V pulse, which translates into a positive pulse, followed by a delay, then a negative pulse.
-We approximated this behavior using piecewise discontinuous step functions (red curve) that was convolved with a 0.6 $\mu$s triangle function to smoothen the step function.
-This produced the blue curve which matched the general shape of the P wave arrival in Figure \ref{fig5}(c).
-We will use this as a forward model to approximate the source-time from the active PZT source.
-We clearly see that the normalized force-time function varies from [-1,1], which is appropriate for our definition of $f^{*}$ in Section \ref{XXX}.
+\subsection{Frequency domain analysis}
+In this section we perform the discrete Fourier transform of the measured and theoretical traces in Figure \ref{fig3}.
+For clarity we only show the results from the sensor A3 shown in Figure \ref{fig5} to illustrate the steps taken to solve for the scaling function $A_{0}$.
+To minimize the uncertainty that can occur from non-uniform spacing of samples of the Fourier frequencies linear scale, we average over multiple bins while evenly spacing our samples on the logarithmic scale.
+We re-sample all DFT on the with 41 samples from 100 kHz to 1000 kHz.
+While this might cause some averaging uncertainties between neighboring frequencies, this does not affect our final estimates of the scaling factor  $A_{0}$ in equation \eqref{eq4c} since, as we will see, we take estimate the scaling factor $A_{0}$ as a single average over the full range of frequencies.
 
-To solve for the scaling function $K(\hat{\omega})$ we need to know the instrument response function $i(t)$.
-For this study, we use the results from \citet{Wu2020}.
-They performed multiple ball drops to create known force-time functions at the same location as the active sensors.
-The same sensors were used in their study and a series of different ball sizes where used (diameters = 0.3 mm, .....to 1.5 mm).
-\citet{Wu2020} modeled long times to also capture how the sensors responded to frequencies as low as $f$ =1 kHz, following the methodology by \citet{Wu2018}.
-Figure \ref{fig6}(a) shows the full instrument response function for each sensor in the Fourier domain (see equation \ref{eq5}).
-Figure \ref{fig6}(b) focuses only on the results for frequencies between $f$ = 100 kHz to 1000 kHz, which is more important to our understanding of the true force-time function in our case.
+Figure \ref{fig7}(a) shows the Fourier transform of the signal ($\mathcal{F}[s] = S$, green line) and instrument response ($\mathcal{F}[i] = I_{k}$, black line) for sensor A3 between frequencies from 100 kHz to 1000 kHz.
+Figure \ref{fig7}(b) shows spectral estimates of the theoretical ground motions $S$ from the signal side, i.e.
+from equation \eqref{eq6}.
+As discussed in Section \label{Spec_deconv}, we can also try to estimate  theoretical ground motions from the source side.
+Figure \ref{fig7}(c) shows the DFT of the empirical Green's function ($\mathcal{F}[g_{kj}] = G_{kj}$, black line) and the normalized force-time function ($\mathcal{F}[f^{*}_{j}] = F^{*}_{j}$, blue line).
+Figure \ref{fig7}(d), shows the spectral estimates of $F_{j}$ determined from using the previous results with equation \eqref{eq6c}.
+The spectral response is relatively flat with a mean value of 3.4 N/Hz for our analysis on sensor A3.
+Using the same approach on all other passive sensors we see an average 3.3 N/Hz with a standard deviation of 0.66 N/Hz.
 
@@
 \includegraphics[scale= 1]{FIG7.pdf} 
-\caption{\textbf{(a)}  }
+\caption{\textbf{(a)} Discrete Fourier transform (DFT) of the measured waveform $S$ (green line) and the instrument response from sensor $I_{k}$ (black line) at A3 between 100 kHz to 1000 kHz.
+\textbf{(b)} Spectral estimates of the ground displacements $U_{k}$ (gray line) obtained from spectral division using equation \eqref{eq6}.
+\textbf{(c)} We show the DFT of the normalized force-time function $F_{j}^{*}$ (blue line) and the empirical Green's function $G_{kj}$ (black line) .
+\textbf{(d)} Spectral estimates of the corrected force time function $F$ calculated from the spectral estimates of the signal, instrument response, Green's function, normalized force time function.
+The spectral mean from between 100 kHz to 1000 kHz is shown.}
 	\label{fig7} 
@@
 
-\begin{figure}[ht]
-     	\centering
-\includegraphics[scale= 1]{FIG8.pdf} 
-\caption{\textbf{(a)}  }
-	\label{fig8} 
-\end{figure}
+Using the calculations highlighted in Figure \ref{fig7}, we use the inverse Discrete Fourier transform (IDFT) to return the force-time function into the time domain.
+Firstly, due to the fact that the frequency response is relatively flat over the 100 kHz to 1000 kHz range (Figure \ref{fig7}(d)) we use the mean spectral value to scale the spectrum of normalized force-time function $F^{*}$ (blue line in Figure \ref{fig7}(c)) prior to performing the IDFT.
+We choose to scale the normalized source time function since, due to properties of the IDFT, we require frequencies outside the range we are able to estimate the spectral calculations shown in Figure \ref{fig7}.
+We note that lower frequencies cannot be studied due to the plate finite geometry that limits our analysis of the signal to 50 $\mu s$.
+In Figure \ref{fig9}(a) we show the broadband DFT of the normalized force-time function (blue line).
+We scale this with the scaling factor from Figure \ref{fig7}(d) to obtain the re-scaled force-time function in the Fourier domain $F$ (black line).
+We have also applied a 4-pole bandpass butterworth filter (red line) between 100 kHz and 1000 kHz, which will be used in our time domain comparison between synthetic estimates to the filtered and unfiltered signals.
+Figure \ref{fig9}(b) shows the IDFT to our estimates of the normalized (blue), unfiltered (black) and filtered (red) signals.
+The corrected force-time function in the time domain estimates that the peak force of $\sim$ 3.4 N.
+This estimate fall within a reasonable range of estimated force-time function for conical sensor estimate by \citet{Breckenridge1990} $\sim $ 1.2 N for a transient step function over 1 $\mu s$ with an amplitude of 100 V.
+We note that if the systems studied by \citet{Breckenridge1990} was linear, for a 200 V we would expect a 2.4 N step.
+While there are discrepancies, the exact details of the conical PZT (geometry, casing, backing mass, damping material, etc.) are not given so it is difficult to perfectly characterize the discrepancies.
+Moreover, the voltage-time function that excited the PZT actuator differs in each study; we employ a pulse-discharge excitation, whereas they employed a step-hold.
 
@@
 \end{figure}
+
+\subsection{Synthetic reconstructing}
 

### 2020-04-30 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 
-\title{A methodology for calculating active source-time functions from broadband piezoelectric sensors in the laboratory}
+\title{A methodology for calculating active force-time functions from broadband piezoelectric sensors}
 
@@
 \begin{keyword}
-Acoustic emissions, physical acoustics, non-destructive testing, active source methods
+Acoustic emissions,  piezoelectric sensors, absolute source calibration 
 \end{keyword}
@@
 
-Understanding wave elastodynamic waves propagate through a medium has proven to have a multitude of applications in many fields of science and engineering.  
-\\
+Understanding the theory associated with elastodynamic wave propagation in materials has proven to be highly applicable to many disciplines in science and engineering.
+The general principle follows that by measuring the kinematic motion at a point in/on the media, perturbed by the incoming elastic waves, we can use wave propagation theory to back calculate critical information.
+The particle motions within the body are governed by the wave equation and the body itself can be solid or fluid materials and the waves carry both information of the media in which they propagate and of the source which caused them.
+This concept has made for many practical and highly interdisciplinary application.
+It has been widely applied in the fields of seismology, biomedicine, and nondestructive testing, to name a few.
 
-Application in material science (crack detection), biomedics (ultrasonics), \textbf{more?} 
-\\
-The premise is to use well-understood physics associated with wave propagation, in fluids or solids media, to probe properties and assess its state in a non-destructive manner.
+The concept relies heavily on understanding attributes to three key components: (\textit{i}) source, (\textit{ii}) material and (\textit{iii}) receiver.
+In most applications, these waves are non-intrusive, propagating elastically through the medium from the source to receiver.
+From this, the problem benefits from \textit{source-receiver reciprocity} and due to symmetry of the wave equation, \textit{time invariance} applies, making this a versatile and flexible tool.
 
-\\\
+Sources can occur due to anthropogenic forcing, for example, rock samples subjected to outside stresses in a laboratory setting can crack locally, generating acoustic emissions \citep[e.g.][]{Lei2014}.
+These emission cause vibrations within sample using peizoelectric sensors in the laboratory.
+This phenomena also scales up to mining activities where microseismic studies are performed to ensure safety during engineering activities \citep[e.g.][]{Manthei2018}.
+Further up the scale, that large earthquakes occurring on faults in nature, occur naturally, activated by slow tectonic loading on geologic timescale.
+At each scale, the physic governing wave propagation holds and the vibrations through the medium are studied with arrays of sensors that are sensitive to vibrations at a range of frequencies.
+When the sources occur due to spontaneous instability, we consider this to be passive monitoring.
 
-The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
-To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources.
-We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.
-By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty.
-We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
+Sources can also be actively imposed, meaning that a transient force must manufactured within or on the body of interest.
+Since the wave equation still governs the resulting motions throughout the body, it becomes an important tool to study the material properties or changes them over time.
+Moreover, if multiple sources can be manufactured, understanding structures becomes possible through, for example, tomographic inversion.
+This has been particularly important in the medical industry, where ultrasonic sensors can act as source or receivers and structures within the body can non-invasively be reconstructed through ultrasound computer tomography (USCT) \citep[e.g.][]Christensen1988}.
+While this methods assume that acoustic waves propagate (i.e.
+fluid), \textit{active field survey} in geophysics assume that the material is a solid and can reconstruct the subsurface to a high degree of certainty using `shot gather' approach and having well-constrained and repeatable sources.
 
+In this study, we aim to study properties of ab active source produced in a controlled laboratory setting.
+Active survey in the laboratory have been employed for decades and typically study vibrations in the range of 100 kHz to 5 MHz.
+Many source can be manufactured from pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive \citep{Breckenridge1990}.
+As stated above, understanding attributes of the source is paramount to gaining more insight of the material it samples with the elastic waves.
+We aim to better understand the exact nature of the transient force produced when a rapid voltage transient is applied to a conical piezoelectric actuator.
+However, since direct measurement of this force is not easy at the frequencies required, we aim to infer the force-time function by studying the ground motions on an array of passive sensors.
+To simplify the problem we study the wave propagation problem in a homogeneous and elastic material.
+
+\subsection{Lamb's problem and PZT actuators}
+
+The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1885}.
+More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space.
+These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology.
+These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g.
+ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.).
+We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method.
+This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.
+
+While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
+In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b).
+The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Figure \ref{fig1}.
+The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards.
+In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later).
+For this example, a snapshot of the velocity wave-field, produced from a capillary fracture is shown from numerical finite element simulations in ABAQUS \citep[adapted from fig.
+2][]{Selvadurai2019}.
+
+Properties of the source creating the stress waves is important.
+\citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes.
+He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive, noting that each type is imperfect and has its trade offs.
+In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g.
+trixaial pressure cell).
+To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.
+
+In Figure \ref{fig2}(a), we show the five components of ``toolchain'' that is used to link the source to the measured signal.
+The PZT actuator is used to produce a (\textit{1}) \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$.
+Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be computed using the (\textit{2}) \textbf{Green's function} $G_{kj}$.
+The Green's functions map the (\textit{3})\textbf{ elastic displacements} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$.
+A passive sensor, on the bottom surface at point $\mathbf{x}$ and attempts to measure the theoretical displacements $u_{k}$.
+Unfortunately, the passive sensors always will distort the (\textit{4}) \textbf{measured signal}  $s$ according to its (\textit{5}) \textbf{instrument response} $i_{k}$ at position $\mathbf{x}$ and time $t$.
+
+\begin{figure}[h]
+     	\centering
+\includegraphics[scale= 1.0]{FIG2.pdf} 
+\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function.
+The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}.
+P and S waves are highlighted for reference only.
+The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
+	\label{fig2} 
+\end{figure}
 \section{Experimental facilities}
@@
 Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame.
-Small rummer pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame.
+Small rubber pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame.
 Material properties of the steel plate required to model the wave propagation problem in the steel plate are given in Table \ref{table1}.
@@
 Figure \ref{fig1}(b) show the array holder for the passive sensor (KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source.
-The aluminium array had a 7 $\time$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.
+The aluminium array had a 7 $\times$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.
 In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e.
@@
 
-\subsection{Lamb's problem and PZT actuators}
-
-The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1988}.
-More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space.
-These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology.
-These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g.
-ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.).
-We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method.
-This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.
-
-While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
-In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b).
-The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Figure \ref{fig1}.
-The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards.
-In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later).
-For this example, a snapshot of the velocity wave-field, produced from a capillary fracture is shown from numerical finite element simulations in ABAQUS \citep[adapted from fig.
-2][]{Selvadurai2019}.
-
-Properties of the source creating the stress waves is important.
-\citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes.
-He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive, noting that each type is imperfect and has its trade offs.
-In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g.
-trixaial pressure cell).
-To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.
-
-In Figure \ref{fig2}(a), we show the five components of ``toolchain'' that is used to link the source to the measured signal.
-The PZT actuator is used to produce a (\textit{1}) \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$.
-Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be computed using the (\textit{2}) \textbf{Green's function} $G_{kj}$.
-The Green's functions map the (\textit{3})\textbf{ elastic displacements} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$.
-A passive sensor, on the bottom surface at point $\mathbf{x}$ and attempts to measure the theoretical displacements $u_{k}$.
-Unfortunately, the passive sensors always will distort the (\textit{4}) \textbf{measured signal}  $s$ according to its (\textit{5}) \textbf{instrument response} $i_{k}$ at position $\mathbf{x}$ and time $t$.
-
-developing more understanding of realistic force-time function produced by the PZT actuators has many potential benefits.
-Due to these properties we are able simply study and isolate individual components of the ``toolchain''.
-
-\begin{figure}[h]
-     	\centering
-\includegraphics[scale= 1.0]{FIG2.pdf} 
-\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function.
-The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}.
-P and S waves are highlighted for reference only.
-The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
-	\label{fig2} 
-\end{figure}
-
 \section{Theoretical Framework}
@@
 
-We build on the recent studies of signal analysis and instrument calibration by \citet{McLaksey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}.
+We build on the recent studies of signal analysis and instrument calibration by \citet{McLaskey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}.
 Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our system in a linear time-invariant (LTI) fashion.
@@
 
-\subsection{Time domain characteristics of the Force Function}
+\subsection{Time Domain Characteristics of the Force-Time Function}
 \label{force_time}
@@
 
-Figure \ref{fig7}(a) shows the Fourier transform of the signal ($\mathcal{F}[s] = S$, green line) and instrument response ($\mathcal{F}[i] = I_{k}$, black line) for sensor A3 between frequencies from 100 kHz to 1000 kHz.
-Figure \ref{fig7}(b) shows spectral estimates of the theoretical ground motions $S$ from the signal side, i.e.
-from equation \eqref{eq6}.
-As discussed in Section \label{Spec_deconv}, we can also try to estimate  theoretical ground motions from the source side.
-Figure \ref{fig7}(c) shows the DFT of the empirical Green's function ($\mathcal{F}[g_{kj}] = G_{kj}$, black line) and the normalized force-time function ($\mathcal{F}[f^{*}_{j}] = F^{*}_{j}$, blue line).
-Figure \ref{fig7}(d), shows the spectral estimates of $F_{j}$ determined from using the previous results with equation \eqref{eq6c}.
-The spectral response is relatively flat with a mean value of 3.4 N/Hz for our analysis on sensor A3.
-Using the same approach on all other passive sensors we see an average 3.3 N/Hz with a standard deviation of 0.66 N/Hz.
-
 \begin{figure}[ht]
@@
 \end{figure}
+
+Figure \ref{fig7}(a) shows the Fourier transform of the signal ($\mathcal{F}[s] = S$, green line) and instrument response ($\mathcal{F}[i] = I_{k}$, black line) for sensor A3 between frequencies from 100 kHz to 1000 kHz.
+Figure \ref{fig7}(b) shows spectral estimates of the theoretical ground motions $S$ from the signal side, i.e.
+from equation \eqref{eq6}.
+As discussed in Section \label{Spec_deconv}, we can also try to estimate  theoretical ground motions from the source side.
+Figure \ref{fig7}(c) shows the DFT of the empirical Green's function ($\mathcal{F}[g_{kj}] = G_{kj}$, black line) and the normalized force-time function ($\mathcal{F}[f^{*}_{j}] = F^{*}_{j}$, blue line).
+Figure \ref{fig7}(d), shows the spectral estimates of $F_{j}$ determined from using the previous results with equation \eqref{eq6c}.
+The spectral response is relatively flat with a mean value of 3.4 N/Hz for our analysis on sensor A3.
+Using the same approach on all other passive sensors we see an average 3.3 N/Hz with a standard deviation of 0.66 N/Hz.
 
@@
 \end{figure}
+
+\section{Discussion}
+
+%The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
+To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources.
+We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.
+By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty.
+We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
 

### 2020-05-01 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 \begin{abstract}
-
+We preform active source tests using a piezoelectric (PZT) actuator that was excited by a rapid transient high voltage pulse (HVP).
+The crystal geometry of the actuator was a conical frustum where the tip was placed centrally on top of a thick steel plate.
+We studied the elastodynamic stress waves  (between 100 kHz to 1 MHz) produced by the source, whereby the HVP pulse was converted to a rapid transient force-time function ($f_{j}$) via the piezoelectric effect.
+The source produced mechanical vibrations ($u_{k}$) throughout the sample and was measured ($s$) using an array of 13 passive conical PZT receivers, at known locations on the bottom of the steel plate.
+Dynamic Green's functions ($G_{kj}$) were calculated using generalized ray theory and the known instrument responses ($I_{k}$) were pre-calculated from a series of ball drop experiments for all source-receiver pairs.
+Using these parameters, we were able to reconstruct the force-time function of the PZT actuator.
+As predicted from the literature, the actuator behaved as an under-damped oscillator with a peak loads, decay rate and undamped resonant frequency of $A_{0}$ = 3.3 $\pm$ 0.8 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, respectively.
+Both the decay rate and resonant frequency were determined as by minimizing the error between theoretical displacements for this force-time function over all 13 receiver measurements.
+Understanding calibrated force-time functions from PZT actuators can help to develop time-dependent and nondestructive characterization of many acoustic emission system components, such as the receiving transducers or the transfer media itself, in non-accessible laboratory environments.
 \end{abstract}
@@
 \begin{keyword}
-Acoustic emissions,  piezoelectric sensors, absolute source calibration 
+Laboratory seismology, acoustic emissions,  piezoelectric sensors, absolute source calibration, 
 \end{keyword}
@@
 
-While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
+While more complex sources have been considered to model earthquakes, such as the single and double couple source, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
 In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b).
@@
 In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g.
-trixaial pressure cell).
+triaxial pressure cell).
 To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.
@@
 Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be computed using the (\textit{2}) \textbf{Green's function} $G_{kj}$.
-The Green's functions map the (\textit{3})\textbf{ elastic displacements} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$.
+The Green's functions map the (\textit{3}) \textbf{mechanical vibrations} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$.
 A passive sensor, on the bottom surface at point $\mathbf{x}$ and attempts to measure the theoretical displacements $u_{k}$.
@@
 The aim of this study is to better understand the force produced by the piezoelectric actuator by studying the waves produced at different locations on the bottom of the specimen.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 1.0]{FIG1.pdf} 
+\caption{\textbf{(a)} General schematic of the calibration station located in the Rock Physics and Mechanics Laboratory at ETH Zurich.
+We used apparatus to apply an active source downwards, which was centrally located on the top of a steel platen.
+This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors.
+\textbf{(b)} The array of PZT sensors are shown where the colors indicate their epicentral location with respect to the source and is used throughout the study.
+\textbf{(c)} Driver circuit for pulse source diagram showing the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX).
+\textbf{(d)} The solution for the time-dependent pulse and discharge of the voltage applied across the PZT element using circuit theory.
+}
+	\label{fig1} 
+\end{figure}
 
@@
 
-A total of 13 sensor are used and the spectral characteristics of these sensors have been well examined in the literature using the absolute calibration methods \citep{Glaser1998, McLaskey2010, McLaskey2012, Selvadurai2015, Selvadurai2019, Wu2020}.
+A total of 13 sensor are used and the spectral characteristics of these sensors have been well examined in the literature using the absolute calibration methods \citep{Glaser1998, McLaskey2010, McLaskey2012, Selvadurai2015, Selvadurai2019, Wu}.
 \citet{Glaser1998} provides a detailed account to sensor attributes used by KRN Services, including a the small field emission transistor (FET)-based Sanyo (2SK715W) preamplifier internal to the sensor casing to improve impedance matching.
 These sensors have shown flat displacements-responses between 100 kHz to 1 MHz \citep{McLaskey2012, Selvadurai2019}.
-At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more like accelerometer \citep{Wu2020}.
-
-\begin{figure}[ht]
-     	\centering
-\includegraphics[scale= 1.0]{FIG1.pdf} 
-\caption{\textbf{(a)} General schematic of the calibration station located in the Rock Physics and Mechanics Laboratory at ETH Zurich.
-We used apparatus to apply an active source downwards, which was centrally located on the top of a steel platen.
-This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors.
-\textbf{(b)} The array of PZT sensors are shown where the colors indicate their epicentral location with respect to the source and is used throughout the study.
-\textbf{(c)} Driver circuit for pulse source diagram showing the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX).
-\textbf{(d)} The solution for the time-dependent pulse and discharge of the voltage applied across the PZT element using circuit theory.
-}
-	\label{fig1} 
-\end{figure}
+At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more like accelerometer \citep{Wu}.
 
@@
 In a concerted study, we have predetermined the instrument responses for the exact same sensor configuration shown in Figure \ref{fig1}.
-However, \citet{Wu2020} produced a known force-time function by dropping small steel balls of different diameters onto the surface from a known height at the identical location that will be used for the PZT actuator later.
+However, \citet{Wu} produced a known force-time function by dropping small steel balls of different diameters onto the surface from a known height at the identical location that will be used for the PZT actuator later.
 According to Hertzian contact theory, it is possible to assume a source time function that is a function of the material properties of the ball and steel platen ($E, \nu, \rho$), the radius of ball, and the drop height.
@@
 
-For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu2020} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm.
+For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm.
 The balls had elastic modulii $E_{ball}$ = 210 GPa and Poisson ratio $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}.
@@
 This insensitivity has also been acknowledged in the past for the same KRNPC-BB conical-style sensors used here \citep{Goodfellow2015, Selvadurai2019}.
-Results from this calibration campaign are summarized and more details have been given in \citet{Wu2020}.
+Results from this calibration campaign are summarized and more details have been given in \citet{Wu}.
 
@@
 \includegraphics[scale= 1.0]{FIG6.pdf} 
-\caption{Summary of the calibration experiments performed by \citet{Wu2020} to determine the instrument response for ball drops, performed \textit{a priori}, in the same location as where our PZT actuator was later placed.
+\caption{Summary of the calibration experiments performed by \citet{Wu} to determine the instrument response for ball drops, performed \textit{a priori}, in the same location as where our PZT actuator was later placed.
 \textbf{(a)} The full range of calibrated frequencies (1 kHz to 1 MHz) is shown.
@@
 Colors are indicative of the sensors location as defined in Figure \ref{fig1}(b).
-For all the details please consult \citet{Wu2020}.
+For all the details please consult \citet{Wu}.
 }
@@
 
-\subsection{Spectral Deconvolution of the Problem}
+\subsection{Spectral Deconvolution}
 \label{Spec_deconv}
@@
 \subsection{Time domain analysis}
-A total of 1000 pulses of the PZT actuator were performed but for our results we show a single pulse to show the methodology that follows equations \eqref{eq1} to \eqref{eq6b}.
+To test for source repeatability, we looked a a sweep of 15 pulses of the PZT actuator were performed.
 The source was highly repeatable in at the high-frequencies we investigated.
-From the 1000 tests, the average  Pearson correlation coefficient from the stacked mean was $R$ = \textbf{0.95}.
-In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b) for a random pulse with color indicating different epicentral distances.
-For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen that would occur if longer signals were analyzed.
-The sampling rate was $F_{s}$ = 20 MHz making each trace 1000 samples.
-Since boundary reflections are not considered, we can approximate that the plate is in fact semi-infinite.
-Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
-Figure \ref{fig3}(b) shows the Green's functions at different epicentral locations, moving out from the source at $x$ = 0 mm.
-We call these approximations the empirical Green's function (EGF) since it is a numerical approximation of the true Green's function.
-The true Green's function can be calculated by replacing the force-time function in equatoin \eqref{eq1} with the a unit impulse (Dirac delta) function $\delta_{j}(\mathbf{\xi}, \tau)$.
-In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) from the numerical models.
+From the 13 tests, the Pearson correlation coefficient (PCC) was analysed with respected to the stacked mean.
+We found that the average PCC = 0.9646 $\pm$ 0.03 over all the sensors for the 50 $\mu s$ time window analysed.
+We believe this to be representative of a repeatable source with respect to waveform similarities.
+Our final results will take these deviations into consideration; however, for clarity the results shown in this Section will focus on a single actuator pulse to highlight the methodology described in equations \eqref{eq1} to \eqref{eq6b}.
 
@@
 
+In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b) for a random pulse with color indicating different epicentral distances.
+For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen that would occur if longer signals were analyzed.
+The sampling rate was $F_{s}$ = 20 MHz.
+Since boundary reflections are not considered, we can approximate that the plate is in fact semi-infinite.
+Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
+Figure \ref{fig3}(b) shows the Green's functions at different epicentral locations, moving out from the source at $x$ = 0 mm.
+We call these approximations the empirical Green's function (EGF) since it is a numerical approximation of the true Green's function.
+The true Green's function can be calculated by replacing the force-time function in equatoin \eqref{eq1} with the a unit impulse (Dirac delta) function $\delta_{j}(\mathbf{\xi}, \tau)$.
+In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) from the numerical models.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 0.90]{FIG4.pdf} 
+\caption{Comparison of measurements on sensors A1, A2, A3 and A4 to the emipircal Green's functions calculated using generalized ray theory.
+The KRNBB sensor perform well and capture the wide range of wave phase arrivals.}
+	\label{fig4} 
+\end{figure}
+
 Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.
@@
      	\centering
-\includegraphics[scale= 0.90]{FIG4.pdf} 
-\caption{Comparison of measurements on sensors A1, A2, A3 and A4 to the emipircal Green's functions calculated using generalized ray theory.
-The KRNBB sensor perform well and capture the wide range of wave phase arrivals.}
-	\label{fig4} 
+\includegraphics[scale= 0.85]{FIG5.pdf} 
+\caption{\textbf{(a)} Measurements from sensor A3 (green line) from the active source compared to the EGFs at the same place from the model.
+Detail B looks more closely at the first-arrival P wave.
+\textbf{(b)} Shows the general shape of the P wave (green line) versus the location of the expected P wave arrival (black line) form the Green's function solution.
+From the convolutional nature of the wave propagation problem (equation \eqref{eq1}) we can estimate the general shape of the normalized force-time function $f^{*}_{j}$ shown as the blue line.}
+	\label{fig5} 
 \end{figure}
@@
 
-\begin{figure}[ht]
-     	\centering
-\includegraphics[scale= 0.85]{FIG5.pdf} 
-\caption{\textbf{(a)} Measurements from sensor A3 (green line) from the active source compared to the EGFs at the same place from the model.
-Detail B looks more closely at the first-arrival P wave.
-\textbf{(b)} Shows the general shape of the P wave (green line) versus the location of the expected P wave arrival (black line) form the Green's function solution.
-From the convolutional nature of the wave propagation problem (equation \eqref{eq1}) we can estimate the general shape of the normalized force-time function $f^{*}_{j}$ shown as the blue line.}
-	\label{fig5} 
-\end{figure}
-
 \subsection{Frequency domain analysis}
@@
 We re-sample all DFT on the with 41 samples from 100 kHz to 1000 kHz.
-While this might cause some averaging uncertainties between neighboring frequencies, this does not affect our final estimates of the scaling factor  $A_{0}$ in equation \eqref{eq4c} since, as we will see, we take estimate the scaling factor $A_{0}$ as a single average over the full range of frequencies.
+While this might cause some averaging uncertainties between neighboring frequencies, this does not affect our final estimates of the scaling factor  $A_{0}$ in equation \eqref{eq6c} since, as we will see, we take estimate the scaling factor $A_{0}$ as a single average over the full range of frequencies.
 
@@
      	\centering
-\includegraphics[scale= 1]{FIG7.pdf} 
+\includegraphics[scale= 0.9]{FIG7.pdf} 
 \caption{\textbf{(a)} Discrete Fourier transform (DFT) of the measured waveform $S$ (green line) and the instrument response from sensor $I_{k}$ (black line) at A3 between 100 kHz to 1000 kHz.
@@
 We note that lower frequencies cannot be studied due to the plate finite geometry that limits our analysis of the signal to 50 $\mu s$.
-In Figure \ref{fig9}(a) we show the broadband DFT of the normalized force-time function (blue line).
-We scale this with the scaling factor from Figure \ref{fig7}(d) to obtain the re-scaled force-time function in the Fourier domain $F$ (black line).
-We have also applied a 4-pole bandpass butterworth filter (red line) between 100 kHz and 1000 kHz, which will be used in our time domain comparison between synthetic estimates to the filtered and unfiltered signals.
-Figure \ref{fig9}(b) shows the IDFT to our estimates of the normalized (blue), unfiltered (black) and filtered (red) signals.
-The corrected force-time function in the time domain estimates that the peak force of $\sim$ 3.4 N.
-This estimate fall within a reasonable range of estimated force-time function for conical sensor estimate by \citet{Breckenridge1990} $\sim $ 1.2 N for a transient step function over 1 $\mu s$ with an amplitude of 100 V.
-We note that if the systems studied by \citet{Breckenridge1990} was linear, for a 200 V we would expect a 2.4 N step.
-While there are discrepancies, the exact details of the conical PZT (geometry, casing, backing mass, damping material, etc.) are not given so it is difficult to perfectly characterize the discrepancies.
-Moreover, the voltage-time function that excited the PZT actuator differs in each study; we employ a pulse-discharge excitation, whereas they employed a step-hold.
+
+Figure \ref{fig9}(a) shows the all Fourier frequencies of our synthetic normalized force-time function $F^{*}$ from 20 kHz to 5 MHz (blue).
+Using the scaling factor from Figure \ref{fig7}(d), we can adjust our estimates that corrects our force-time function $F$ (black line) with calibration estimates from the instrument response determined form the ball drop.
+We have also applied a 4-pole bandpass butterworth filter $filt(F)$ (red line) between 100 kHz and 1000 kHz, which will be used in our time domain comparison between synthetic estimates to the filtered and unfiltered signals.
+Figure \ref{fig9}(b) shows the IDFT to our estimates of the normalized (blue), unfiltered (black) and filtered (red) force-time functions.
+The corrected force-time function (black) in the time domain estimates that the peak force of $\sim$ 3.4 N.
 
@@
      	\centering
-\includegraphics[scale= 1]{FIG9.pdf} 
-\caption{\textbf{(a)}  }
+\includegraphics[scale=0.9]{FIG9.pdf} 
+\caption{\textbf{(a)} Discrete Fourier transform (DFT) of the normalized $F^{*}$ (blue line), scaled $F$ (black line) and bandpass filtered $filt(F)$ (red line) of the force time function shown in Figure \ref{fig2b}(d).
+We show scaling factor of 3.4 N/Hz determined from the spectral analysis.
+\textbf{(b)} Inverse discrete Fourier transform (IDFT) of the signals in (a).
+}
 	\label{fig9} 
 \end{figure}
+\subsection{Effects of receiver location on force-time estimates}
 
+To better asses the variations in our estimates of $A_{0}$ with the spatial locations of the receivers we looked at results from all sensors for the 15 pulses.
+Figure \ref{fig9a}(a) shows the estimates of $A_{0}$ with takeoff angle $\theta$.
+The takeoff angle for this setup is depicted in Figure \ref{fig2}.
+Piezoelectric transducers used in the laboratory have been known to be sensitive to incident angle of the incoming waves \citep{Goodfellow2015}.
+This is also seen at the mining scale scale \citep{Kwaitek2011}.
+We see that there is a slight decrease in estimates of $A_{0}$ with increasing  $\theta$, with an average value of 2.3 N.
+
+Figure \ref{fig9a}(b) looks at dependence of $A_{0}$ on the total distance travelled (hypocentral distance).
+Attenuation is the intrinsic loss in energy associated with a cycle of the wave for example by the internal friction of the material.
+By fitting an exponential decay curve we can estimate the materials quality factor $Q$ -- a metric to describe the losses per cycle.
+Our fit finds $A^{*}$ = 4.7 N and $\alpha$ = 0.01.
+Using these parameters we found the average $Q$ = 20,470 between 100 kHz to 1000 kHz, which is acceptable for steel (see Supplemental S2 for more details).
+It is impossible to perfectly determine whether the loss of sensitivity is related to the material property ($Q$) or a sensor characteristics due to the linear dependency of the hypocentral distance on $\theta$, however; material attenuation can explain this decrease with some degree of certainty.
+Taking into account attenuation, the value of the force at the source was $A^{*}$ = 4.7 N.
+This estimate falls within a reasonable range of estimated force-time function for conical sensor by \citet{Breckenridge1990} $\sim $ 1.2 N for a transient step function over 1 $\mu s$ with an amplitude of 100 V.
+If the systems studied by \citet{Breckenridge1990} was linear, we expect that 200 V we would result in a 2.4 N step.
+This discrepancy may results from properties of the system (PZT geometry, casing, backing mass, damping material, electronics, data acquisition system, etc.), which is not identical to our making it difficult to perfectly characterize why they differ discrepancies.
+Moreover, the voltage-time function that excited the PZT actuator differs in each study; we employ a pulse-discharge excitation, whereas they employed a step-hold.
+However, we feel that the similarity in the order of $A_{0}$ is a positive results.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 1]{FIG9a.pdf} 
+\caption{Relationships between spectral estimates of $A_{0}$ and the \textbf{(a)} takeoff angle ($\theta$) and \textbf{(b)} hypocentral distance ($R$).
+An exponential fit was used to determine the quality factor $Q$ (see Supplemental Section S2 for more details)  }
+	\label{fig9a} 
+\end{figure}
 \subsection{Synthetic reconstructing}
+Figure \ref{fig10} shows a comparison of the theoretical ground displacements for the estimated (a) unfiltered and (b) bandpass filtered force-time functions from Figure \ref{fig9}(b).
+To calculate the theoretical displacements we convolve the force-time function with the Green's function following equation \eqref{eq2}.
+We see that the theoretical vibrations match the theory quite we on all sensors.
+This further enforces our hypothesis that the decrease in force estimates on sensors at higher takeoff angles was not a sensor sensitive issue but due to material attenuation.
+Figure \ref{fig10} is a rewarding result from this study and highlights the potential fully understanding the force-time function produced by our PZT actuator and HVP unit.
 
@@
 
-\clearpage
-
+\section{Conclusions}
+We have followed the recently popularized methodology for sensor calibration coupled reasonable understanding of the wave propagation problem in a semi-infinite, homogeneous elastic half space.
+By fully characterizing the individual components of our system, we show that it is possible to better understand the force-produced by a conical PZT actuator when excited by a rapid high-voltage transient.
+While the results presented here are unique to our system, the methodology and insight into the characteristic shape of the force-time function can be easily reproduced in other acoustic emission system.
+Fully understanding how system responses change during an experiment is critical to properly interpret seismicity in a quantitative manner.
+Our approach for time-dependent updates to calibration parameters but also can provide intrinsic and quantitative understanding of changes in the transfer media.
 \section*{Acknowledgement}
@@
 
+\clearpage
 \section*{Supplemental information}
+
+\subsection{Material Properties of PZT-5A (Navy II)}
 
@@
 
+\clearpage
+\subsection{S2 Quality Factor}
+We estimate the quality factor in steel $Q_{steel}$ from estimates of the force magnitude $A_{0}$ at different hypocentral distances.
+This follow typical theory on attenuation used to model the damping of seismic waves over distance due to internal intrinsic losses (e.g.
+friciton) in the material that decreased the energy per cycle\citep[e.g.][]{Barton2007}.
+From Figure \ref{fig9}(b) we have fit the exponential decay over distance with $A^{*}$ = 4.7 N and $\alpha$ = 0.01 m$^{-1}$.
+The quality factor depends on the frequencies of the propagating wave and can be expressed as a function as follows
+
+\begin{equation}
+    \label{eqS2}
+Q = \frac{\pi f}{V_{P}\alpha}.
+\end{equation}
+
+\noindent We can plot the quality factor over the frequency range 100 kHz to 1 MHz investigated in this study for $\alpha$ = 0.01 m$^{-1}$.
+Typical values of $Q_{steel} > $ 10,000 in the literature \citep{WaitingRUI}.
+Figure \ref{figS1} shows that at $f$ =100 kHz $Q$ = 5193, a relatively low estimate, and at $f$ = 1 MHz $Q$ = 51,935, which is a higher estimate for steel.
+Assume a constant attenuation quality factor of the range of 100 kHz to 1 MHz we obtain a average $Q$ = 20,470.
+
+\begin{figure}[ht]
+     	\centering
+\includegraphics[scale= 1]{FIGS1.pdf} 
+\caption{\textbf{(a)}  }
+	\label{figS1} 
+\end{figure}
+
 \end{document}
+
 \endinput

### 2020-05-01 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 Using these parameters, we were able to reconstruct the force-time function of the PZT actuator.
-As predicted from the literature, the actuator behaved as an under-damped oscillator with a peak loads, decay rate and undamped resonant frequency of $A_{0}$ = 3.3 $\pm$ 0.8 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, respectively.
+As predicted from the literature, the actuator behaved as an under-damped oscillator with a peak loads, decay rate and undamped resonant frequency of $A_{0}$ = 4.7 $\pm$ 0.8 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, respectively.
 Both the decay rate and resonant frequency were determined as by minimizing the error between theoretical displacements for this force-time function over all 13 receiver measurements.
@@
 Understanding the theory associated with elastodynamic wave propagation in materials has proven to be highly applicable to many disciplines in science and engineering.
-The general principle follows that by measuring the kinematic motion at a point in/on the media, perturbed by the incoming elastic waves, we can use wave propagation theory to back calculate critical information.
-The particle motions within the body are governed by the wave equation and the body itself can be solid or fluid materials and the waves carry both information of the media in which they propagate and of the source which caused them.
-This concept has made for many practical and highly interdisciplinary application.
+The general principle follows that by measuring the kinematic motion at a point in/on the media as its perturbed by the incoming elastic waves, we can use wave propagation theory to back calculate critical information of the problem.
+The particle motions within the body are governed by the wave equation and the body itself can be a solid or fluid materials.
+The waves carry both information of the media in which they propagate and of the source which caused them.
+This concept has made for many practical and highly interdisciplinary applications.
 It has been widely applied in the fields of seismology, biomedicine, and nondestructive testing, to name a few.
 
-The concept relies heavily on understanding attributes to three key components: (\textit{i}) source, (\textit{ii}) material and (\textit{iii}) receiver.
+The concept relies heavily on understanding attributes to three key components: (\textit{i}) source, (\textit{ii}) material and (\textit{iii}) receiver as shown in Figure \ref{fig2}.
 In most applications, these waves are non-intrusive, propagating elastically through the medium from the source to receiver.
-From this, the problem benefits from \textit{source-receiver reciprocity} and due to symmetry of the wave equation, \textit{time invariance} applies, making this a versatile and flexible tool.
+From this, the problem benefits from \textit{source-receiver reciprocity} and due to symmetry of the wave equation, \textit{time invariance} applies, making this a versatile and flexible problem.
 
-Sources can occur due to anthropogenic forcing, for example, rock samples subjected to outside stresses in a laboratory setting can crack locally, generating acoustic emissions \citep[e.g.][]{Lei2014}.
-These emission cause vibrations within sample using peizoelectric sensors in the laboratory.
+Sources can occur due to anthropogenic forcing, for example, rock samples subjected to outside stresses in a laboratory setting can crack locally, generating acoustic emissions \citep[e.g.][]{Lei2014, Moradian2016}.
+These emission cause vibrations within sample and these are recorded using peizoelectric sensors at known locations.
 This phenomena also scales up to mining activities where microseismic studies are performed to ensure safety during engineering activities \citep[e.g.][]{Manthei2018}.
-Further up the scale, that large earthquakes occurring on faults in nature, occur naturally, activated by slow tectonic loading on geologic timescale.
+Further up the scale, large natural earthquakes on faults are activated by slow tectonic loading on geologic timescale.
 At each scale, the physic governing wave propagation holds and the vibrations through the medium are studied with arrays of sensors that are sensitive to vibrations at a range of frequencies.
@@
 Sources can also be actively imposed, meaning that a transient force must manufactured within or on the body of interest.
-Since the wave equation still governs the resulting motions throughout the body, it becomes an important tool to study the material properties or changes them over time.
-Moreover, if multiple sources can be manufactured, understanding structures becomes possible through, for example, tomographic inversion.
-This has been particularly important in the medical industry, where ultrasonic sensors can act as source or receivers and structures within the body can non-invasively be reconstructed through ultrasound computer tomography (USCT) \citep[e.g.][]Christensen1988}.
-While this methods assume that acoustic waves propagate (i.e.
-fluid), \textit{active field survey} in geophysics assume that the material is a solid and can reconstruct the subsurface to a high degree of certainty using `shot gather' approach and having well-constrained and repeatable sources.
+Since the wave equation still governs the motions throughout the body, it becomes an important tool to study the material properties or changes in them over time.
+Moreover, if multiple sources can be manufactured at varied locations, it becomes possible to understand structures through, for example, tomographic inversion.
+This has been particularly important in the medical industry, where ultrasonic sensors can act as source or receivers and structures within the subject can be non-invasively reconstructed through ultrasound computer tomography (USCT) \citep[e.g.][]{Christensen1988}.
+While medical applications assume that acoustic waves propagate (i.e.
+fluid), \textit{active field surveys} in geophysics assume that the material is a solid and can reconstruct the subsurface to a high degree of certainty using `shot gather' approach and having well-constrained and repeatable sources.
 
@@
 
-The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1885}.
+The study of waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1885}.
 More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space.
-These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology.
+These early studies aimed to understand wave phase arrivals and their relationship to earthquake sources in the field of seismology.
 These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g.
-ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.).
+ch 6 in][]{Aki2002}.
+These studies vary in complexity, for example in the media (in-homogeneous layered, or anisotropic, etc.), with the sources (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.).
 We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method.
-This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.
+This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been implemented in a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.
 
 While more complex sources have been considered to model earthquakes, such as the single and double couple source, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).
-In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b).
-The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Figure \ref{fig1}.
+In Figure \ref{fig2}(a), we show the cross-section of the problem at hand.
+The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Section \ref{ExpFac}.
 The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards.
-In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later).
-For this example, a snapshot of the velocity wave-field, produced from a capillary fracture is shown from numerical finite element simulations in ABAQUS \citep[adapted from fig.
+In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the wave-field we study here.
+This snapshot of the velocity wave-field represents that produced from a capillary fracture and was solved using a numerical finite element approach in ABAQUS \citep[adapted from fig.
 2][]{Selvadurai2019}.
@@
 \citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes.
-He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive, noting that each type is imperfect and has its trade offs.
-In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g.
+He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive.
+He noted that each type is imperfect and has its trade offs.
+In this study, we look to aim to understand the PZT actuator (similar their conical transducer) which we can be leverage to non-invasively study the \textit{in situ} conditions inside less accessible experimental facility (e.g.
 triaxial pressure cell).
@@
 
-In Figure \ref{fig2}(a), we show the five components of ``toolchain'' that is used to link the source to the measured signal.
-The PZT actuator is used to produce a (\textit{1}) \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$.
-Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be computed using the (\textit{2}) \textbf{Green's function} $G_{kj}$.
-The Green's functions map the (\textit{3}) \textbf{mechanical vibrations} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$.
-A passive sensor, on the bottom surface at point $\mathbf{x}$ and attempts to measure the theoretical displacements $u_{k}$.
-Unfortunately, the passive sensors always will distort the (\textit{4}) \textbf{measured signal}  $s$ according to its (\textit{5}) \textbf{instrument response} $i_{k}$ at position $\mathbf{x}$ and time $t$.
+In Figure \ref{fig2}, we show the five components of ``toolchain'' that is used to link the source to the measured signal and governed by the wave equation.
+The PZT actuator is used to produce (\textit{1}) a \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$.
+Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be solved for using (\textit{2}) \textbf{Green's function} $G_{kj}$.
+The Green's functions map the (\textit{3}) \textbf{mechanical vibrations} $u_{k}$ at point $\mathbf{x}$ and time $t$ to the force at point $\mathbf{\xi}$ and time $\tau$.
+A passive sensor on the bottom surface at point $\mathbf{x}$ attempts to measure the theoretical displacements $u_{k}$.
+Unfortunately, all passive sensors distort the (\textit{4}) \textbf{measured signal}  $s$.
+This distortion can be quantified according to its (\textit{5}) \textbf{instrument response} $i_{k}$.
 
@@
 \caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function.
-The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}.
+The velocity field is shown for reference only and was adopted from \citet{Selvadurai2019}.
 P and S waves are highlighted for reference only.
@@
 \section{Experimental facilities}
+\label{ExpFac}
 \subsection{General}
@@
 We study elastodynamic waves propagating through an elastic isotropic, homogeneous steel plate.
-Using an electro-mechanical piezocomposite actuator, deliver impulsive sources on to the top surface of the steel specimen.
-On the bottom, an array of 13 piezoelectric (lead zirconate titanate, PZT) transducers are mounted in an aluminium array holder.
+Using an electro-mechanical piezoelectric actuator, we deliver an impulsive transient source to the top surface of the steel specimen.
+An array of 13 piezoelectric (lead zirconate titanate, PZT) transducers are mounted on the  in an aluminium array holder.
 The aim of this study is to better understand the force produced by the piezoelectric actuator by studying the waves produced at different locations on the bottom of the specimen.
@@
 \includegraphics[scale= 1.0]{FIG1.pdf} 
-\caption{\textbf{(a)} General schematic of the calibration station located in the Rock Physics and Mechanics Laboratory at ETH Zurich.
-We used apparatus to apply an active source downwards, which was centrally located on the top of a steel platen.
-This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors.
-\textbf{(b)} The array of PZT sensors are shown where the colors indicate their epicentral location with respect to the source and is used throughout the study.
-\textbf{(c)} Driver circuit for pulse source diagram showing the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX).
-\textbf{(d)} The solution for the time-dependent pulse and discharge of the voltage applied across the PZT element using circuit theory.
+\caption{\textbf{(a)} General schematic of the sensor calibration station at the Rock Physics and Mechanics Laboratory at ETH Zurich.
+We use this apparatus to apply an active source downwards using a PZT actuator located centrally on the top of a steel plate.
+This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors on the bottom of the plate.
+\textbf{(b)} The array of passive PZT sensors are shown where the colors indicate their epicentral location with respect to the source and these colors used throughout the study.
+\textbf{(c)} The driver circuit for voltage pulse that shows the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX).
+\textbf{(d)} The solution for the time-dependent voltage pulse and discharge applied across the PZT element.
 }
@@
 When excited by a impulsive source, the crystal will resonate sinusoidal at its fundamental frequency and the wave will decay based in internal, external and transmitted losses.
-The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped spring-mass damper system shown in Figure \ref{fig2b](c).
+The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped spring-mass damper system shown in Figure \ref{fig2b}(c).
 \citet{Breckenridge1990} also showed evidence of under-damped behavior when exciting a conical PZT on an aluminium plate.
@@
 
-%The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
+Will complete later.  The discussion in this type of study is not that important I believe.
+
+\textcolor{red}{The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies.
 To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources.
@@
 By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty.
-We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.
+We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.}
 
@@
 Our approach for time-dependent updates to calibration parameters but also can provide intrinsic and quantitative understanding of changes in the transfer media.
+
 \section*{Acknowledgement}
-T. M\"orgeli
+The authors are indebted to the work and enthusiasm of Mr.
+T.
+M\"orgeli.
+He has been instrumental in the development of the infrastructure and provided critical input, design strategy and workmanship for the PZT actuator and the calibration station.
+His work is supported through the Rock Physics and Mechanics Laboratory at ETH Zurich.
+
+Mr. Wu has been supported financially by China Scholarship Council (CSC, No. 201806440037).
+
+Dr. Selvadurai has was funded under FILL IN ASK STEFAN.
+
+Dr. Madonna was funded ...
+
+Dr. Moradian was funded ...
 
@@
 
-\subsection{Material Properties of PZT-5A (Navy II)}
-
+\*subsection{Material Properties of PZT-5A (Navy II) }
 \begin{table}[ht]
@@
 \clearpage
-\subsection{S2 Quality Factor}
+\subsection*{S2 Quality Factor}
 We estimate the quality factor in steel $Q_{steel}$ from estimates of the force magnitude $A_{0}$ at different hypocentral distances.

### 2020-05-01 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame.
-Small rubber pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame.
-Material properties of the steel plate required to model the wave propagation problem in the steel plate are given in Table \ref{table1}.
+Small rubber pads (5 mm $\times$ 5 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame.
+Material properties of the steel plate required to model the wave propagation problem are given in Table \ref{table1}.
 Centrally located on the top surface is a piezoelectric actuator built in-house.
@@
 \noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatic theory.
-Figure \ref{fig1}(b) show the array holder for the passive sensor (KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source.
-The aluminium array had a 7 $\times$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.
+
+Figure \ref{fig1}(b) show the array holder for the passive PZT sensor (KRN Services model: KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source.
+The aluminium array had a 7 $\times$ 7 locations with 23 mm spacing in both the $1$- and $2$-directions.
 In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e.
-aligned in the $3$-direction) and, therefore, have focused most of our sensors converge to one quadrant.
-Similar colors of the sensors locations in Figure \ref{fig1}(b), represents similar epicentral locations.
-We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and have shown that there appear to be little to no directivity in the active source.
+aligned in the $3$-direction) and, therefore, have focused most of our passive sensors converge to one quadrant of the array holder.
+Similar colors of the sensors locations in Figure \ref{fig1}(b), represents their epicentral locations.
+We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and we show in Section \ref{results} that there appears to be little to no misalignment of the active source.
 
 A total of 13 sensor are used and the spectral characteristics of these sensors have been well examined in the literature using the absolute calibration methods \citep{Glaser1998, McLaskey2010, McLaskey2012, Selvadurai2015, Selvadurai2019, Wu}.
-\citet{Glaser1998} provides a detailed account to sensor attributes used by KRN Services, including a the small field emission transistor (FET)-based Sanyo (2SK715W) preamplifier internal to the sensor casing to improve impedance matching.
+\citet{Glaser1998} provides a detailed account to sensor attributes.
+This sensor includes a the small field emission transistor (FET)-based (Sanyo model: 2SK715W) that preamplifies internally to improve impedance matching and loss due to wire capacitance.
 These sensors have shown flat displacements-responses between 100 kHz to 1 MHz \citep{McLaskey2012, Selvadurai2019}.
-At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more like accelerometer \citep{Wu}.
+At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more similar to an accelerometer \citep{Wu}.
 
@@
 
-We build on the recent studies of signal analysis and instrument calibration by \citet{McLaskey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}.
-Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our system in a linear time-invariant (LTI) fashion.
-This assumes that changes in the sensor and source behavior and material properties are unaffected over time.
-We assume point representations of both the sensor and source location, which might be influenced so-called ``aperture'' effect.
-However, this is minimized by using the point contact conical PZT crystal, which will be discussed later when we examine in more detail how the force systems of passive and active PZT sensors.
+We build on the recent studies of signal analysis and instrument calibration by \citet{McLaskey2012} and continuing our analysis using Green's function formalization \citep{Aki2002, Johnson1974}.
+Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our linear time-invariant (LTI) system.
+This approach assumes that changes in the sensor and source behavior and material properties are unaffected over time.
+We assume point representations at both the sensor and source location, which might be influenced so-called ``aperture'' effect.
+However, this is minimized by using a smaller contact point characteristic of the conical frustum PZT crystal, which will be discussed later when we examine in more detail how the force systems of the PZT actuator.
 
-Using the classical theory describing dynamic elasticity \citep{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$.
+Using the classical theory describing dynamic elasticity \citep{Aki2002}, we use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$.
 This is given as the convolution of the force with the Green's function
@@
 
-\noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.
+\noindent We note that $\ast$ represents convolution in the time domain, subscripts reflect Einstein summation convention, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.
 For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties.

### 2020-05-01 Article_file_Source_reconstruction.tex
Updates from Overleaf

@@
 
-\noindent We note that $\ast$ represents convolution in the time domain, subscripts reflect Einstein summation convention, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$.
+\noindent We note that $\ast$ represents convolution in the time domain, subscripts reflect Einstein summation convention, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u_{k}$ at location $\mathbf{x}$.
 For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties.
-The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ or the identity convolution.
+The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ also known as the identity convolution.
 
@@
 We can relate the true surface displacement $u_{k}$ to voltage measurement $s$ using the instrument response, which is given as
+
    \begin{equation}
@@
 
-    \noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the forces which produced them:
+    \noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the force which produced them:
 
@@
 
-\noindent We can also use this formulation to relate the measured signals to a set of self-equilibrating forces or moments $m_{jp}$ \citep{Aki2002}.
-Displacements in the body are related to the spatial derivative of the elastodynamic Green's function $g_{kj,p}$.
+\noindent We can also use this formulation to relate the measured signals to a set of self-equilibrating force couples or moments $m_{jp}$ \citep{Aki2002} but this is not necessary here.
 While this is more similar to sources buried within a specimen and may be more representative of an earthquake source, this is not the focus of this study.
-In this study, all sources are produced on the surface of the specimen, which justifies the use of only equation \eqref{eq2}.
+In this study, all sources are produced on the surface of the specimen, which justifies the use of equation \eqref{eq2}.
 
@@
 
-\noindent where $f^{*}_{j}$ is the normalized force-time function that has units (N) and a general shape to that follows the electro-mechanical behavior of the coupled high-voltage discharge and sensor systems.
-A unitless scaling factor $\kappa(\tau)$ will be used to scale the normalized force time-function $f^{*}$ to the true force-time function $f$ and likely varies with the time as the electrical pulse is applied to the active source.
+\noindent where $f^{*}_{j}$ is the normalized force-time function is unitless ($\cdot$) and a general shape to that follows the electro-mechanical behavior of the coupled high-voltage discharge and sensor system.
+A scaling factor $A_{0}$ will be used to scale the normalized force time-function $f_{j}^{*}$ to the true force-time function $f_{j}$ and is an important parameter to quantitatively interpret the PZT actuator behavior.
 
@@
 \includegraphics[scale= 0.9]{FIG2b.pdf} 
-\caption{\textbf{(a)} Enhanced view of the contact region from the concial PZT actuator.
-\textbf{(b)} Simplified schematic showing the electro-mechanical systems and the estimate region where a pressure pulse $p_{j}$ (red) is generated when excited by the impulsive voltage.
-We assume that the force-time $f_{j}$ (blue arrow) is simply the integration of transient pressure over a constant circular contact area $A_{contact}$ and acting only in the 3-direction.
-\textbf{(c)} Model summarizing the complex behavior of the PZT actuator (both internal and external) using an under-damped spring-mass damper systems whose behavior follow equation \eqref{eq4b}.
+\caption{\textbf{(a)} An enhanced view of the contact region between the PZT actuator and steel specimen.
+\textbf{(b)} A simplified schematic showing the electro-mechanical systems and the hypothesised region where the pressure pulse $p_{j}$ (red) is applied.
+We assume that the force-time $f_{j}$ (blue arrow) is simply the integration of transient pressure over a constant circular contact area $A_{contact}$ and acts only in the 3-direction.
+\textbf{(c)} Under-damped oscillator we use to describe response of the PZT actuator to the HVP.
 \textbf{(d)} The normalized force-time function for: $A_{0}$ = 1 N, $\Gamma$ = 0 MHz and $\Lambda$ = 4.7 MHz (black line) and $A_{0}$ = 1 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz (blue line).}
@@
 In Figure \ref{fig2b}(a) we look in detail at the position where the PZT actuator contacts steel plate.
-The actuator has threads on its body and is loaded on the plate by applying a small torque where the conical PZT tip is loaded through a thin layer of nickel (0.03 mm thick).
-This nickel foil is the cathode of the electro-mechanical circuit shown in Figure \ref{fig2b}(b), which represent a more detailed representation of the PZT actuator mentioned in the driver circuit (see Figure \ref{fig1}(c)).
-A small amount of contact gel is used to improve contact between the nickel cathode and steel plate but nickel was chosen due to is malleability and it formed a strong contact with the steel platen under minimal pressure \citep{Glaser1998}.
-To better understand the transient point force $f_{j}$ applied, we consulted literature in the biomedical industry that has studied piezomaterial, with similar pulsed excitation voltages, to perform ultrasonic reconstruction in acoustic media.
+The actuator has threads on its body and is loaded on the plate by applying a small torque.
+Where the conical PZT tip contacts the plate, it loads through a thin layer of nickel (0.03 mm thick) and a thin layer of contact gel.
+This nickel foil is the cathode of the electro-mechanical circuit shown in Figure \ref{fig1}(c).
+A small amount of contact gel is used to improve contact between the nickel cathode and steel plate but nickel was chosen due to is malleability and it forms clean contact to the steel plate under minimal pressure \citep{Glaser1998}.
+
+To better understand the transient point force $f_{j}$ , we consulted literature in the biomedical industry that has a large repository of literature on piezomaterial, specifically its behavior when pulsed with rapid transient voltages similar to our case.
+This problem is well-known due to its application for ultrasonic reconstruction in acoustic media.
 \citet{Christensen1988} looked at the pressure caused by a an electrical circuit that generated a sharp voltage pulse similar to that shown in Figure \ref{fig1}(d).
@@
 \cite{Christensen1988} found that the transient response of the pressure did not precisely duplicate the waveform of the voltage (see Figure \ref{fig1}(b)) due to the resonant properties of the crystal.
-When excited by a impulsive source, the crystal will resonate sinusoidal at its fundamental frequency and the wave will decay based in internal, external and transmitted losses.
-The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped spring-mass damper system shown in Figure \ref{fig2b}(c).
-\citet{Breckenridge1990} also showed evidence of under-damped behavior when exciting a conical PZT on an aluminium plate.
+When excited by a impulsive source, the crystal will resonate sinusoidal at its fundamental frequency and the wave will decay based on internal, external and transmitted losses.
+The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped oscillator system shown in Figure \ref{fig2b}(c).
+While this behavior was observed for a fluid transfer media, it is clear that similar behavior was seen by\citet{Breckenridge1990} when exciting a conical PZT on an aluminium plate.
 
-\citet{Christensen1988} notes that the damping of the pressure will be inversely proportional to the mechanical loss factor of the PZT crystal, but we argue that more variables might be contributing to this of the coupling of all the internal component such as the backing mass material and shape, they connections between the internal electrically conductive components, the shape of the crystal, the type of potting agent, the amount of coupling gel used, the type of material being pulsed (fluid or elastic), amongst other features \citep{Glaser1998}.
-We argue that attempting to solve the full systems behavior with all these complexities is counter productive to the crux of this study.
-By the properties of convolution describing the wave propagation in equations \eqref{eq1}, we can assume that the measured signals will still have the general shape of the normalized force-time $f^{*}$ embedded in the measurements.
+\citet{Christensen1988} notes that the damping of the pressure will be inversely proportional to the mechanical loss factor of the PZT crystal, but we argue that more variables might be contributing to this of the coupling of all the internal component such as the backing mass material and shape, the electrical connections, the shape of the crystal, the type of potting agent, or external such as the amount of coupling gel used, the type of material being pulsed (fluid or elastic), amongst other features \citep{Glaser1998}.
+We argue that attempting to solve the full systems behavior -- with all these complexities -- is counter productive to the crux of this study.
+By the properties of convolution describing the wave propagation in equations \eqref{eq1}, we can assume that the measured signals will still exhibit the general shape of the normalized force-time $f^{*}$ within the measurements about the phase arrivals.
 We generalized the normalized force time function shown in Figure \ref{fig2b}(d) as follows
@@
 
-\noindent where $A_{0}$ is the scaling factor (= 1 N for the normalized case), $\Gamma$ and $\Lambda$ are the decay and vibration parameters of the normalized force-time function.
-We note that the subscript $_{j}$ has disappears since we are assuming that the normalized force is acting only in the $`3'$-direction.
-Later, we will describe how these two parameters are used in an inversion to minimize the errors between the theoretical displacements $u_{k}$ and measured signals $s$ over all the measured sensors.
-For the case in Figure \ref{fig2b}(d), $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, which represented the best-fit solution for our analysis of the specific PZT used in this study following the excitation pulse in Figure \ref{fig1}(d).
+\noindent where $A_{0}$ is the scaling factor (= 1 N for the normalized case), $\Gamma$ and $\Lambda$ are the decay and resonant parameters.
+We note that the subscript $_{j}$ has disappears since we are assuming that the normalized force is acting only in the '$3$'-direction.
+Later, we will describe how these two parameters are calculated by means of an inversion to minimize the errors between the theoretical displacements $u_{k}$ and measured signals $s$ over all the measured sensors.
+The blue waveform shown in Figure \ref{fig2b}(d), where $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, represented the best-fit solution of our analysis.
 
@@
 
-We use properties of the Fourier transform \citep{Bracewell1986} to help deconvolve equations \eqref{eq3} and \eqref{eq4}.
-In the frequency domain, convolution and deconvolution simply becomes multiplication and division.
+We use properties of the Fourier transform \citep{Bracewell1986} to help the time-domain equations \eqref{eq3} and \eqref{eq4}.
+In the frequency domain, convolution and deconvolution simply becomes multiplication and division, respectively.
 This allows us to isolate the components of interest we wish to quantify for our analysis.
@@
 \noindent where $I_{k}$, $S$, $F_{j}$ and $G_{kj}$ are calculated from the temporal Fourier transforms of the $i_{k}$, $s$, $f_{j}$ and $g_{kj}$, respectively.
-In a concerted study, we have predetermined the instrument responses for the exact same sensor configuration shown in Figure \ref{fig1}.
-However, \citet{Wu} produced a known force-time function by dropping small steel balls of different diameters onto the surface from a known height at the identical location that will be used for the PZT actuator later.
-According to Hertzian contact theory, it is possible to assume a source time function that is a function of the material properties of the ball and steel platen ($E, \nu, \rho$), the radius of ball, and the drop height.
-This method has been popularized over the recent years due to a highly reliable and repeatable force-time function $f$ produced from ball impact and the ability to absolutely calibrate the acoustic emission sensors over a wide spectral range \citep{Breckenridge1990, McLaskey2010, McLaskey2012, McLaskey2015}.
+In a concerted study, we have predetermined the instrument responses for the exact same sensor configuration shown in Figure \ref{fig1}(d).
+To do so \citet{Wu} produced a known force-time function by dropping a range small steel balls of different diameters onto the surface from a known height at the identical location that is be used for the PZT actuator here.
+According to Hertzian contact theory, it is possible to model a source time function, which depends on the material properties of the ball and steel platen ($E, \nu, \rho, E_{ball}, \nu_{ball}, \rho_{ball}$), the radius of ball ($r_{ball}$) and the drop height ($h$).
+This method has been popularized over the recent years due to its high reliability and repeatable.
+It is considered to be a simple manner to absolutely calibrate acoustic emission sensors over a wide spectral range \citep{Breckenridge1990, McLaskey2010, McLaskey2012, McLaskey2015}.
 
-For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm.
-The balls had elastic modulii $E_{ball}$ = 210 GPa and Poisson ratio $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}.
-Once the force-time function is know, we use equation \eqref{eq5}, now with $F_{ball}\left( \mathbf{\xi}, \omega \right)$, which represents the Fourier transform of the ball drop, to calculate the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.
+For the identical source-receiver configuration shown in Figure \ref{fig1}(b), \citet{Wu} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm from $h$ = ???
+drop height.
+The balls had elastic modulii $E_{ball}$ = 210 GPa and Poisson ratio $\nu_{ball}$ = 0.303, which allow them to calculate the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}.
+Once the force-time function is know, they used equation \eqref{eq5}, now substituting $F_{ball}\left( \mathbf{\xi}, \omega \right)$ for the force-time function.
+This allowed them to understand the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.
 Calculating the lower frequency instrument response (i.e.
-1 kHz to 50 kHz ) is not straightforward and the readers should also consult \citet{Wu2018} for a summary of methods.
+1 kHz to 50 kHz ) is not straightforward and the readers should consult \citet{Wu2018} for a summary of methods.
 Figure \ref{fig6}(a) shows the full instrument response for all the passive sensors shown in Figure \ref{fig1}(b).
 The color coding related to the sensors epicentral distance from the ball drop source.
-In this study, we are only interested in the higher frequency (100 kHz to 1 MHz) sensor behavior for the reconstruction of the PZT actuator force time function.
+In this study, we are only interested in the higher frequency (100 kHz to 1 MHz) behavior for the reconstruction of the PZT actuator force-time function.
 This range is shown in Figure \ref{fig6}(b).
@@
 \label{Spec_deconv}
-Having the specific broadband instrument response, solved using the well-understood ball drop source for our exact sensor-source layout, is paramount to accurately model the force-time function of the PZT actuator described by equation \eqref{eq4b}.
-If we now consider the original problem in Figure \ref{fig2}, we can start with the recorded signal produced from the PZT actuator and use the instrument response to determined the mechanical vibration.
+Having the sensor specific broadband instrument response, solved for our exact sensor-receiver layout, is paramount to accurately model the force-time function of the PZT actuator described by equation \eqref{eq4b}.
+If we now reconsider the original problem in Figure \ref{fig2}, we can start with the recorded signal produced from the PZT actuator and use the instrument response to determine the mechanical vibration.
 In the Fourier domain, we can rearrange the left hand side of equation \eqref{eq3} to estimate the spectral response of the theoretical vibration $U_{k}(\mathbf{x},t)$ caused by the transient PZT actuator:
@@
 
-Approaching the problem from the source side (right hand side of equation \eqref{eq3}), we can estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is shown as:
+Conversely, we can approaching the problem from the source side (right hand side of equation \eqref{eq3}) and estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is described as:
 
@@
 
-\noindent Substituting the Fourier transform of the force-time function describe in equation \eqef{eq4}, we obtain
+\noindent Substituting the Fourier transform of the force-time function describe in equation\eqef{eq4}, we obtain
 
@@
 \noindent where the Fourier transform of the force-time magnitude parameter is $\mathcal{F}[A_{0}] = A_{0}\cdot\delta(\omega)$ and $\delta$ is the Dirac delta function.
-Next we can combine equations \eqref{eq6} and \eqref{eq6b} to solve for the scaling factor for the force-time function $A_{0}$:
+Next we can combine equations \eqref{eq6} and \eqref{eq6b} to isolate the force-time function of the PZT actuator:
 
@@
 \subsection{Time domain analysis}
-To test for source repeatability, we looked a a sweep of 15 pulses of the PZT actuator were performed.
+To test for source repeatability, we looked at a sweep of 15 pulses of the PZT actuator.
 The source was highly repeatable in at the high-frequencies we investigated.
-From the 13 tests, the Pearson correlation coefficient (PCC) was analysed with respected to the stacked mean.
+From the 13 tests, the Pearson correlation coefficient (PCC) was analysed with respected to the stacked mean of the 15 pulse.
 We found that the average PCC = 0.9646 $\pm$ 0.03 over all the sensors for the 50 $\mu s$ time window analysed.
-We believe this to be representative of a repeatable source with respect to waveform similarities.
-Our final results will take these deviations into consideration; however, for clarity the results shown in this Section will focus on a single actuator pulse to highlight the methodology described in equations \eqref{eq1} to \eqref{eq6b}.
+We believe this to be representative of a repeatable source simply due to waveform similarities.
+Our final results will take these deviations into consideration; however, for clarity, we will continue to the results from a single actuator pulse to highlight the methodology described in equations \eqref{eq1} to \eqref{eq6b}.
 
@@
 \caption{\textbf{(a)} Measurements taken from the passive PZT transducers from a single transient PZT excitation described in Figure \ref{fig1}(d).
-The color scheme represents the different epicentral locations of each sensor in Figure \ref{fig1}(b).
-\textbf{(b)} Green's function solutions determined using generalized ray theory for a semi-infinite elastic, homogeneous steel plate at different epicentral locations.
-We see the various phase arrival predicted from the model.}
+The color scheme represents the different epicentral locations.
+\textbf{(b)} Green's function solutions determined using the numerical generalized ray theory for a semi-infinite, elastic and homogeneous steel plate at increasing epicentral distances.
+Various wave phase arrival predicted by the model are shown.}
 	\label{fig3} 
@@
 
-In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b) for a random pulse with color indicating different epicentral distances.
+In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors for a random pulse.
 For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen that would occur if longer signals were analyzed.
 The sampling rate was $F_{s}$ = 20 MHz.
-Since boundary reflections are not considered, we can approximate that the plate is in fact semi-infinite.
-Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
+Since boundary reflections are not considered, we can treat the steel specimen as semi-infinite.
+Under this assumption, we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.
 Figure \ref{fig3}(b) shows the Green's functions at different epicentral locations, moving out from the source at $x$ = 0 mm.
 We call these approximations the empirical Green's function (EGF) since it is a numerical approximation of the true Green's function.
-The true Green's function can be calculated by replacing the force-time function in equatoin \eqref{eq1} with the a unit impulse (Dirac delta) function $\delta_{j}(\mathbf{\xi}, \tau)$.
+The true Green's function can be calculated by replacing the force-time function in equation \eqref{eq1} with the a unit impulse (Dirac delta) function $\delta_{j}(\mathbf{\xi}, \tau)$.
 In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) from the numerical models.
@@
 
-Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.
+Figure \ref{fig4} compares the empirical Green's function (EGF) $g_{kj}$ to the measured signals $s$.
 For clarity, we only show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) at epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively.
 We see that the sensors captures various phase arrivals predicted form the model.
-The ability of these sensors to accurately capture wave arrivals and information even at high azimuthal incident angles has been discussed in the literature \citep{Goodfellow2015, Selvadurai2019} and is due to the conical geometry of the PZT crystal.
+The ability of these sensors to accurately capture wave arrivals and information even at high azimuthal incident angles has been discussed in the literature \citep{Goodfellow2015, Selvadurai2019} and is believed to be due to the conical geometry of the PZT crystal.
 
@@
 We see that there appears to be some similarities in our measured signals that would justify our hypothesized force-time function given in equation \eqref{eq4b}.
-While the fit is not perfect -- the signal sensor A3 appears to a lower decay parameter $\Gamma$ -- this will be addressed when we simultaneously invert to match these variables on all sensors.
-Before doing so, we must calculate the scaling factor in the frequency domain using equation \eqref{eq6c}.
+While the fit is not perfect -- the signal sensor A3 appears to a lower decay parameter $\Gamma$ -- the similarities are convincing enough to continue our analysis.
+To do so we must employ the Fourier analysis from Section \ref{Spec_deconv}.
 
 \subsection{Frequency domain analysis}
-In this section we perform the discrete Fourier transform of the measured and theoretical traces in Figure \ref{fig3}.
-For clarity we only show the results from the sensor A3 shown in Figure \ref{fig5} to illustrate the steps taken to solve for the scaling function $A_{0}$.
+In this section we perform discrete Fourier transforms of the measured and theoretical traces which are shown in Figure \ref{fig3}.
+Again, for calrity, we only show the results from the sensor A3 shown in Figure \ref{fig5} to best illustrate the steps taken.
 To minimize the uncertainty that can occur from non-uniform spacing of samples of the Fourier frequencies linear scale, we average over multiple bins while evenly spacing our samples on the logarithmic scale.
 We re-sample all DFT on the with 41 samples from 100 kHz to 1000 kHz.
-While this might cause some averaging uncertainties between neighboring frequencies, this does not affect our final estimates of the scaling factor  $A_{0}$ in equation \eqref{eq6c} since, as we will see, we take estimate the scaling factor $A_{0}$ as a single average over the full range of frequencies.
+While this might cause some averaging uncertainties between neighboring frequencies, this does not affect our final estimates of the scaling factor in equation \eqref{eq6c} since, as we will see, we take estimate the scaling factor $A_{0}$ as a single average over the full range of studied frequencies.
 
@@
 Figure \ref{fig7}(a) shows the Fourier transform of the signal ($\mathcal{F}[s] = S$, green line) and instrument response ($\mathcal{F}[i] = I_{k}$, black line) for sensor A3 between frequencies from 100 kHz to 1000 kHz.
-Figure \ref{fig7}(b) shows spectral estimates of the theoretical ground motions $S$ from the signal side, i.e.
+Figure \ref{fig7}(b) shows spectral estimates of the theoretical ground motions $U_{k}$  (gray line) when approached from the signal side, i.e.
 from equation \eqref{eq6}.
-As discussed in Section \label{Spec_deconv}, we can also try to estimate  theoretical ground motions from the source side.
+As discussed in Section \label{Spec_deconv}, we can can independently estimate theoretical ground motions from the source side.
 Figure \ref{fig7}(c) shows the DFT of the empirical Green's function ($\mathcal{F}[g_{kj}] = G_{kj}$, black line) and the normalized force-time function ($\mathcal{F}[f^{*}_{j}] = F^{*}_{j}$, blue line).
-Figure \ref{fig7}(d), shows the spectral estimates of $F_{j}$ determined from using the previous results with equation \eqref{eq6c}.
-The spectral response is relatively flat with a mean value of 3.4 N/Hz for our analysis on sensor A3.
-Using the same approach on all other passive sensors we see an average 3.3 N/Hz with a standard deviation of 0.66 N/Hz.
+Figure \ref{fig7}(d), shows the spectral estimates of $F_{j}$ (magenta line) determined from using the previous results with equation \eqref{eq6c}.
+The spectral response is relatively flat with a mean value of 3.4 N/Hz for this analysis of a single pulse measured at sensor A3.
+Using the same approach on all other passive sensors we see an average 3.3 N/Hz with a standard deviation of 0.66 N/Hz but this will be discussed in Section \ref{All_sensors}.
 
-Using the calculations highlighted in Figure \ref{fig7}, we use the inverse Discrete Fourier transform (IDFT) to return the force-time function into the time domain.
-Firstly, due to the fact that the frequency response is relatively flat over the 100 kHz to 1000 kHz range (Figure \ref{fig7}(d)) we use the mean spectral value to scale the spectrum of normalized force-time function $F^{*}$ (blue line in Figure \ref{fig7}(c)) prior to performing the IDFT.
-We choose to scale the normalized source time function since, due to properties of the IDFT, we require frequencies outside the range we are able to estimate the spectral calculations shown in Figure \ref{fig7}.
-We note that lower frequencies cannot be studied due to the plate finite geometry that limits our analysis of the signal to 50 $\mu s$.
+Using the results from Figure \ref{fig7}, we use the inverse Discrete Fourier transform (IDFT) to return the force-time function into the time domain.
+Firstly, due to the fact that the frequency response of $F_{j}$ is relatively flat over the 100 kHz to 1000 kHz range (Figure \ref{fig7}(d)), we use the mean spectral value to scale the spectrum of normalized force-time function $F_{j}^{*}$ (blue line in Figure \ref{fig7}(c)) prior to performing the IDFT.
+We choose to scale the normalized source time function since, due to properties of the IDFT where we require more Fourier frequencies that reside outside the pertinent range of this analysis.
+Due to smooth mathematical description of the force-time shape given by equation \eqref{eq4b}, we can extend our analysis to lower frequencies since this feature is not affected by the finiteness of the plate.
+We note that lower frequencies cannot be studied for our waveforms in this analysis, due to the specimen finiteness, which limits our signals to 50 $\mu s$.
 
 Figure \ref{fig9}(a) shows the all Fourier frequencies of our synthetic normalized force-time function $F^{*}$ from 20 kHz to 5 MHz (blue).
-Using the scaling factor from Figure \ref{fig7}(d), we can adjust our estimates that corrects our force-time function $F$ (black line) with calibration estimates from the instrument response determined form the ball drop.
-We have also applied a 4-pole bandpass butterworth filter $filt(F)$ (red line) between 100 kHz and 1000 kHz, which will be used in our time domain comparison between synthetic estimates to the filtered and unfiltered signals.
+Using the scaling factor from Figure \ref{fig7}(d), we can adjust our estimates to correct the magnitude of the true force-time function $F$ (black line).
+We have also applied a 4-pole bandpass butterworth filter $filt(F)$ (red line) between 100 kHz and 1000 kHz, which will be used in our time domain comparison between unfiltered and filtered ground motion predictions and raw signals.
 Figure \ref{fig9}(b) shows the IDFT to our estimates of the normalized (blue), unfiltered (black) and filtered (red) force-time functions.
-The corrected force-time function (black) in the time domain estimates that the peak force of $\sim$ 3.4 N.
+The corrected force-time function (black) in the time domain estimates that the peak force of $\sim$ 3.4 N for this specific source-receiver pair.
 
@@
 \subsection{Effects of receiver location on force-time estimates}
+\label{All_sensors}
 
-To better asses the variations in our estimates of $A_{0}$ with the spatial locations of the receivers we looked at results from all sensors for the 15 pulses.
-Figure \ref{fig9a}(a) shows the estimates of $A_{0}$ with takeoff angle $\theta$.
-The takeoff angle for this setup is depicted in Figure \ref{fig2}.
+To better asses the variations in our estimates of $A_{0}$ with the spatial locations of the receivers we looked at results from all 13 passive PZT sensors for the 15 pulses.
+Figure \ref{fig9a}(a) shows the relationship between $A_{0}$ and the takeoff angle $\theta$.
+The takeoff angle for this experiment is depicted as $\theta$ in Figure \ref{fig2}.
 Piezoelectric transducers used in the laboratory have been known to be sensitive to incident angle of the incoming waves \citep{Goodfellow2015}.
@@
 Figure \ref{fig9a}(b) looks at dependence of $A_{0}$ on the total distance travelled (hypocentral distance).
-Attenuation is the intrinsic loss in energy associated with a cycle of the wave for example by the internal friction of the material.
-By fitting an exponential decay curve we can estimate the materials quality factor $Q$ -- a metric to describe the losses per cycle.
-Our fit finds $A^{*}$ = 4.7 N and $\alpha$ = 0.01.
-Using these parameters we found the average $Q$ = 20,470 between 100 kHz to 1000 kHz, which is acceptable for steel (see Supplemental S2 for more details).
-It is impossible to perfectly determine whether the loss of sensitivity is related to the material property ($Q$) or a sensor characteristics due to the linear dependency of the hypocentral distance on $\theta$, however; material attenuation can explain this decrease with some degree of certainty.
-Taking into account attenuation, the value of the force at the source was $A^{*}$ = 4.7 N.
-This estimate falls within a reasonable range of estimated force-time function for conical sensor by \citet{Breckenridge1990} $\sim $ 1.2 N for a transient step function over 1 $\mu s$ with an amplitude of 100 V.
-If the systems studied by \citet{Breckenridge1990} was linear, we expect that 200 V we would result in a 2.4 N step.
-This discrepancy may results from properties of the system (PZT geometry, casing, backing mass, damping material, electronics, data acquisition system, etc.), which is not identical to our making it difficult to perfectly characterize why they differ discrepancies.
-Moreover, the voltage-time function that excited the PZT actuator differs in each study; we employ a pulse-discharge excitation, whereas they employed a step-hold.
-However, we feel that the similarity in the order of $A_{0}$ is a positive results.
+Attenuation is the intrinsic loss in energy associated with a cycle of the wave that occurs from, for example the internal friction of the material.
+By fitting an exponential decay curve $A_{0} = A^{*}exp[-\alpha\cdot R]$ to estimate the materials quality factor $Q$ -- a metric to describe the losses per cycle \citep{Barton2007}.
+Our fit (red line) finds $A^{*}$ = 4.7 N and $\alpha$ = 0.01.
+Using these parameters we found the average $Q$ = 20,470 between 100 kHz to 1000 kHz, which is acceptable for steel \citep{citation}.
+Details of how we calculated $Q$ are described in Supplemental S2.
+In our experiment it is unfortunately impossible to perfectly decouple these trends in these parameters.
+To determine whether the loss of sensitivity is related to the material property ($Q$) or a sensor characteristics is influenced the linear dependency of one to the other.
+However, there is evidence that material attenuation can explain this decrease with some degree of certainty.
+If we accept our hypothesis that attenuation is valid, we estimate the force at the source is $A^{*}$ = 4.7 N.
+This estimate falls within a reasonable range of estimates of the amplitude of force generated by pulsing a for conical sensor by \citet{Breckenridge1990}.
+They found $\sim $ 1.2 N for a transient step-voltage with a rise time of over 1 $\mu s$ with an amplitude of 100 V.
+If their systems was linear, we could expect that 200 V we would result in a 2.4 N step.
+While this is still has discrepancy, the results likely depend highly on properties of the system (PZT geometry, PZT material, sensor casing, backing mass, damping material, electronic system, cable used, data acquisition system, etc.), which is not identical -- making it difficult to perfectly characterize differences.
+Moreover, the voltage-time function that excited the PZT actuator differ in each study; we employ a pulse-discharge excitation, whereas they employed a step-hold voltage.
+We feel that the similarity in the order of $A_{0}$ is a positive results that comes from our analysis.
 
@@
 Figure \ref{fig10} shows a comparison of the theoretical ground displacements for the estimated (a) unfiltered and (b) bandpass filtered force-time functions from Figure \ref{fig9}(b).
-To calculate the theoretical displacements we convolve the force-time function with the Green's function following equation \eqref{eq2}.
-We see that the theoretical vibrations match the theory quite we on all sensors.
+For Figure \ref{fig10}(b), both the predicted gorund motions and signal have been filtered using the same 4-pole butterworth bandpass used earlier.
+To calculate the theoretical displacements the force-time function is convolved with the Green's function following equation \eqref{eq2}.
+We see that the theoretical vibrations (black line) match the signals (colored lines) quite well.
 This further enforces our hypothesis that the decrease in force estimates on sensors at higher takeoff angles was not a sensor sensitive issue but due to material attenuation.
-Figure \ref{fig10} is a rewarding result from this study and highlights the potential fully understanding the force-time function produced by our PZT actuator and HVP unit.
+Each theoretical estimate has been convolved with its appropriate force-time function with unique scaling factor.
+This takes into account attenuation in a implicit manner.
+Figure \ref{fig10} is a rewarding result from this study and highlights the potential fully understanding the force-time function produced by a PZT actuator and HVP unit.
 
@@
 \includegraphics[scale= 1]{FIG10.pdf} 
-\caption{\textbf{(a)}  }
+\caption{\textbf{(a)} Unfiltered theoretical estimates of ground motions (black lines) compared to raw measurements of the passive PZT array (colored lines).
+\textbf{(b)} Filtered theoretical estimates of ground motions (black lines) compared to filtered measurements of the passive PZT array (colored lines).
+}
 	\label{fig10} 
@@
 
-Dr. Selvadurai has was funded under FILL IN ASK STEFAN.
+Dr. Selvadurai was funded ...
 
@@
 Dr. Moradian was funded ...
-
-\bibliographystyle{elsarticle-harv} 
-\bibliography{Source_reconstruction}
 
@@
 \end{figure}
+\clearpage
+\bibliographystyle{elsarticle-harv} 
+\bibliography{Source_reconstruction}
 
